### 2023-01-24 src/ms.tex
brought paper up to first compilable state

\documentclass[twocolumn,linenumbers]{src/aastex631}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\usepackage{amsmath}
\usepackage{cancel}
\usepackage{float}

\shorttitle{Self Consistently Modeling NGC 2808}
\shortauthors{Boudreaux et al.}
% \watermark{DRAFT}
\graphicspath{{./}{figures/}{src/figures}}

\begin{document}

\title{Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.}

\correspondingauthor{Thomas M. Boudreaux}
\email{thomas.m.boudreaux.gr@dartmouth.edu, thomas@boudreauxmail.com}

\author[0000-0002-2600-7513]{Thomas M. Boudreaux}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\author[0000-0003-3096-4161]{Brian C. Chaboyer}
\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}

\author[0000-0002-2012-7215]{Gregory Feiden}
\affiliation{Department of Physics and Astronomy, University of North Georgia, Dahlonega, GA 30533, USA}

\begin{abstract}
	Over its approximately 100 year history stellar modeling has become an
	essential tool for understanding certain astrophysical phenomena which are not
	directly observable. Modeling allows for empirical constraints --- such as
	elemental abundances, luminosities, and effective temperatures --- to strongly
	inform non-observables such as a star's age, mass, and radius. Here we propose a
	thesis in five parts, related through their use of both modeling and the
	Dartmouth Stellar Evolution Program (DSEP) to conduct this modeling. In two of
	the parts of this thesis we will use DSEP, in conjunction with atmospheric
	boundary conditions generated by collaborators, to build chemically
	self-consistent models of multiple populations (MPs) in the globular clusters
	NGC 2808, 47 Tuc, and NGC 6752. We will infer helium abundances across MPs and
	compare these inferred abundances to those from models which do not consider as
	careful a handling of a star's chemistry. PLACEHOLDER
\end{abstract}

\keywords{}

\input{src/sections/intro.tex}

\begin{acknowledgments}
	This work has made use of the NASA astrophysical data system (ADS). We
	would like to thank Elisabeth Newton and Aaron Dotter for their support and
	for useful disscusion related to the topic of this paper. We acknowledge
	the support of a NASA grant (No. 80NSSC18K0634). 
\end{acknowledgments}

% \software{
% 	The Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008},
% 	\texttt{FreeEOS} \citep{Irwin2012},
% 	\texttt{pyTOPSScrape} \citep{Boudreaux22}
% }

\bibliography{src/bib/ms}{}
\bibliographystyle{aasjournal}

\end{document}

### 2023-01-24 src/sections/intro.tex
brought paper up to first compilable state

\section{Introduction}\label{sec:Intro}
Introduction

### 2023-01-24 src/sections/intro.tex
Added (placeholder) intro pulled from thesis proposal and basic bibliography file contents for GC

@@
 \section{Introduction}\label{sec:Intro}
-Introduction
+Whereas, people have have often tried to categorized objects as GCs by making
+cuts along half-light radius, density, and surface brightness profile, in fact
+many objects which are generally thought of as GCs don't cleanly fit into these
+cuts. Consequently, \citet{Carretta2010} proposed a definition of GC based on
+observed chemical inhomogeneities in their stellar populations. The modern
+understanding of GCs then is not simply one of a dense cluster of stars which
+may have chemical inhomogeneities and multiple populations; rather, it is one
+where those chemical inhomogeneities and multiple populations themselves are
+the defining element of a GC.
+
+All globular clusters older than 2 Gyr studied in detail show populations
+enriched in He, N, and Na while also being deplete in O and C
+\citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
+not strongly correlated with variations in heavy element abundances. One
+consequence of this fact is the spectroscopically uniform Fe abundances
+mentioned in \S\ref{sec:intro_GC}. Further, high-resolution spectral studies
+reveal anti-correlations between N-C abundances, Na-O abundances, and
+potentially Al-Mg \citep{Sneden1992, Gratton2012}. Typical stellar fusion
+reactions can deplete core oxygen; however, the observed abundances of Na, Al,
+and Mg cannot be explained by the likes of the CNO cycle \citep{Prantzos2007}.
+
+Formation channels for these multiple populations remain a point of debate
+among astronomers. Most proposed formation channels consist of some older,
+more massive, population of stars polluting the pristine cluter media before a
+second population forms, now enriched in heavier elements which they themselves could
+not have generated \citep[for a detailed review see ][]{Gratton2012}. The four
+primary candidates for these polluters are asymptotic giant branch stars
+\citep[AGBs,][]{Ventura2001,DErcole2010}, fast rotating massive stars
+\citep[FRMSs,][]{Decressin2007}, super massive stars
+\citep[SMSs,][]{Denissenkov2014}, and massive interacing binaries
+\citep[MIBs,][]{deMink2009, Bastian2018}.
+
+Hot hydrogen burning (proton capture), material transport to the surface, and
+material ejection into the intra-cluster media are features of each of these
+models and consequently they can all be made to {\it qualitatively} agree with
+the observed elemental abundances. However, none of the standard models can
+currently account for all specific abundances \citep{Gratton2012}. AGB and FRMS
+models are the most promising; however, both models have difficulty reproducing
+severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
+models require signifigant mass loss ($\sim 90\%$) between cluster formation
+and the current epoch --- implying that a signifigant fraction of halo stars
+formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.
+
+In addition to the light-element anti-correlations observed it is also known
+that younger populations are signifigantly enhanced in Helium
+\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
+mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
+However, due to the relatively high and tight temperature range of partial
+ionization for He it cannot be observed in globular clusters; consequently, the
+evidence for enhanced He in GCs originates from comparison of theoretical
+stellar isochrones to the observed color-magnitude-diagrams of globular
+clusters. Therefore, a careful handling of chemistry is essential when modeling
+with the aim of discriminating between MPs; yet, only a very limited number of
+GCs have yet been studied with chemically self-consistent (structure and
+atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.
+
+This thesis will contain chapters where we expand the number of clusters which
+have been self-consistently modeled. In this chapter we will focus on
+chemically self-consistent modeling of the two extreme population of NGC 2808
+identified by \citep{Milone2015}, A and E.
+
+One key element of NGC 2808 modeling is the incorporation of new atmospheric
+models, generated from the \texttt{MARCS} grid of model atmospheres \citep{Plez2008},
+which match interior elemental abundances. \texttt{MARCS} provides one-dimensional,
+hydrostatic, plane-parallel and spherical LTE atmopsheric models
+\citep{Gustafsson2008}. Members of our collaboration have generated atmospheric 
+models for populations A and E.  Integration of these new model atmospheres
+into DSEP is ongoing.
+
+\subsubsection{Population Opacities}
+For similar reasons as discussed in \S\ref{sec:p1} we conduct this research
+with OPLIB high-temperature opacity tables as opposed to OPAL tables. We will
+also generate low temperature opacity tables using the \texttt{MARCS}.
+Moreover, we confirm that the atmosphere and structure meet in an optically
+thick region of the star by shifting the atmospheric fitting point from an optical
+depth of $\tau = 2/3$ (used by DSEP currently for \texttt{PHOENIX} model atmospheres) to
+some higher $\tau$. We will experiment to identify the best optical depth to
+fit at..
+
+These population have been studied in depth by Feiden and their chemical
+compositions were determined in \citet{Milone2015} (see Table 2 in that paper).
+While we cannot yet evolve DSEP models with these new boundary conditions, we
+can make a first pass investigation of the affect of OPLIB opacities (Figure
+\ref{fig:NGC2808ISO}). Note how the models generated using OPLIB opacity tables
+have a systematically lower luminosity. This discrepancy is consistent with
+the overall lower opacities of the OPLIB tables.
+
+\subsubsection{Additional Consistency}
+The isochrones generally used to infer the degree of helium enhancements assume that
+convection operates in the same manner in metal-poor stars as it does in the
+Sun. However, observations from \textit{Kepler} of metal-poor red giants
+\citep{Bonaca2012, tayar2017correlation}, in concert with interferometric
+radius determination of the metal-poor sub-giant HD 140283
+\citep{creevey2015benchmark}, have shown that the efficiency of convection
+changes with iron content. As the final portion of our work to more carefully
+handle a star's chemistry, we will modify DSEP to capture this variation in
+convective efficiency.

### 2023-01-26 src/sections/intro.tex
Started cleaning up introduction

@@
 \section{Introduction}\label{sec:Intro}
-Whereas, people have have often tried to categorized objects as GCs by making
-cuts along half-light radius, density, and surface brightness profile, in fact
-many objects which are generally thought of as GCs don't cleanly fit into these
-cuts. Consequently, \citet{Carretta2010} proposed a definition of GC based on
-observed chemical inhomogeneities in their stellar populations. The modern
-understanding of GCs then is not simply one of a dense cluster of stars which
-may have chemical inhomogeneities and multiple populations; rather, it is one
-where those chemical inhomogeneities and multiple populations themselves are
-the defining element of a GC.
+Globular clusters (GCs) are among the oldest observ- able objects in the
+universe \citep{Pen11}. They are characterized by high densities with typical
+half-light radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses
+ranging from $10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs
+are signifigantly larger than these typical values {\color{red}EXAMPLE}. GCs
+provide a unique way to probe stellar evolution \citep{Bau03}, galaxy formation
+models \citep{Boy18,Kra05}, and dark matter halo struc- ture \citep{Hud18}.
+{\color{red} BRING IN SOME MORE RECENT CITATIONS.}
 
-All globular clusters older than 2 Gyr studied in detail show populations
-enriched in He, N, and Na while also being deplete in O and C
+Whereas, people have have often tried to categorized objects as GCs through
+relations between half-light radius, density, and surface brightness profile,
+in fact many objects which are generally thought of as GCs don't cleanly fit
+into these cuts {\color{red} EXAMPLE + CITATION}. Consequently,
+\citet{Carretta2010} proposed a definition of GC based on observed chemical
+inhomogeneities in their stellar populations. The modern understanding of GCs
+then is not simply one of a dense cluster of stars which may have chemical
+inhomogeneities and multiple populations; rather, it is one where those
+chemical inhomogeneities and multiple populations themselves are the defining
+element of a GC.
+
+All Milky Way globular clusters older than 2 Gyr studied in detail show
+populations enriched in He, N, and Na while also being deplete in O and C
 \citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
-not strongly correlated with variations in heavy element abundances. One
-consequence of this fact is the spectroscopically uniform Fe abundances
-mentioned in \S\ref{sec:intro_GC}. Further, high-resolution spectral studies
-reveal anti-correlations between N-C abundances, Na-O abundances, and
-potentially Al-Mg \citep{Sneden1992, Gratton2012}. Typical stellar fusion
-reactions can deplete core oxygen; however, the observed abundances of Na, Al,
-and Mg cannot be explained by the likes of the CNO cycle \citep{Prantzos2007}.
+not strongly correlated with variations in heavy element abundance, resulting
+in spectroscopically uniform Fe abundances between populations. Further,
+high-resolution spectral studies reveal anti-correlations between N-C
+abundances, Na-O abundances, and potentially Al-Mg \citep{Sneden1992,
+Gratton2012}. Typical stellar fusion reactions can deplete core oxygen;
+however, the observed abundances of Na, Al, and Mg cannot be explained by the
+likes of the CNO cycle \citep{Prantzos2007}.
 
@@
 among astronomers. Most proposed formation channels consist of some older,
-more massive, population of stars polluting the pristine cluter media before a
+more massive, population of stars polluting the pristine cluster media before a
 second population forms, now enriched in heavier elements which they themselves could

### 2023-01-26 src/sections/intro.tex
Finished first pass introduction, split off some stuff into a modeling section

@@
 GCs have yet been studied with chemically self-consistent (structure and
-atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.
-
-This thesis will contain chapters where we expand the number of clusters which
-have been self-consistently modeled. In this chapter we will focus on
-chemically self-consistent modeling of the two extreme population of NGC 2808
-identified by \citep{Milone2015}, A and E.
-
-One key element of NGC 2808 modeling is the incorporation of new atmospheric
-models, generated from the \texttt{MARCS} grid of model atmospheres \citep{Plez2008},
-which match interior elemental abundances. \texttt{MARCS} provides one-dimensional,
-hydrostatic, plane-parallel and spherical LTE atmopsheric models
-\citep{Gustafsson2008}. Members of our collaboration have generated atmospheric 
-models for populations A and E.  Integration of these new model atmospheres
-into DSEP is ongoing.
-
-\subsubsection{Population Opacities}
-For similar reasons as discussed in \S\ref{sec:p1} we conduct this research
-with OPLIB high-temperature opacity tables as opposed to OPAL tables. We will
-also generate low temperature opacity tables using the \texttt{MARCS}.
-Moreover, we confirm that the atmosphere and structure meet in an optically
-thick region of the star by shifting the atmospheric fitting point from an optical
-depth of $\tau = 2/3$ (used by DSEP currently for \texttt{PHOENIX} model atmospheres) to
-some higher $\tau$. We will experiment to identify the best optical depth to
-fit at..
-
-These population have been studied in depth by Feiden and their chemical
-compositions were determined in \citet{Milone2015} (see Table 2 in that paper).
-While we cannot yet evolve DSEP models with these new boundary conditions, we
-can make a first pass investigation of the affect of OPLIB opacities (Figure
-\ref{fig:NGC2808ISO}). Note how the models generated using OPLIB opacity tables
-have a systematically lower luminosity. This discrepancy is consistent with
-the overall lower opacities of the OPLIB tables.
-
-\subsubsection{Additional Consistency}
-The isochrones generally used to infer the degree of helium enhancements assume that
-convection operates in the same manner in metal-poor stars as it does in the
-Sun. However, observations from \textit{Kepler} of metal-poor red giants
-\citep{Bonaca2012, tayar2017correlation}, in concert with interferometric
-radius determination of the metal-poor sub-giant HD 140283
-\citep{creevey2015benchmark}, have shown that the efficiency of convection
-changes with iron content. As the final portion of our work to more carefully
-handle a star's chemistry, we will modify DSEP to capture this variation in
-convective efficiency.
+atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}. Here we present new,
+chemically self-consistent modeling og the two extreme populations of NGC 2808
+identified by \citet{Milone2015}, A and E.

### 2023-01-26 src/sections/modeling.tex
Finished first pass introduction, split off some stuff into a modeling section

\section{Modeling}\label{sec:modeling}
One key element of NGC 2808 modeling is the incorporation of new atmospheric
models, generated from the \texttt{MARCS} grid of model atmospheres \citep{Plez2008},
which match interior elemental abundances. \texttt{MARCS} provides one-dimensional,
hydrostatic, plane-parallel and spherical LTE atmopsheric models
\citep{Gustafsson2008}. Members of our collaboration have generated atmospheric 
models for populations A and E.  Integration of these new model atmospheres
into DSEP is ongoing.

For similar reasons as discussed in \S\ref{sec:p1} we conduct this research
with OPLIB high-temperature opacity tables as opposed to OPAL tables. We will
also generate low temperature opacity tables using the \texttt{MARCS}.
Moreover, we confirm that the atmosphere and structure meet in an optically
thick region of the star by shifting the atmospheric fitting point from an optical
depth of $\tau = 2/3$ (used by DSEP currently for \texttt{PHOENIX} model atmospheres) to
some higher $\tau$. We will experiment to identify the best optical depth to
fit at..

These population have been studied in depth by Feiden and their chemical
compositions were determined in \citet{Milone2015} (see Table 2 in that paper).
While we cannot yet evolve DSEP models with these new boundary conditions, we
can make a first pass investigation of the affect of OPLIB opacities (Figure
\ref{fig:NGC2808ISO}). Note how the models generated using OPLIB opacity tables
have a systematically lower luminosity. This discrepancy is consistent with
the overall lower opacities of the OPLIB tables.

The isochrones generally used to infer the degree of helium enhancements assume that
convection operates in the same manner in metal-poor stars as it does in the
Sun. However, observations from \textit{Kepler} of metal-poor red giants
\citep{Bonaca2012, tayar2017correlation}, in concert with interferometric
radius determination of the metal-poor sub-giant HD 140283
\citep{creevey2015benchmark}, have shown that the efficiency of convection
changes with iron content. As the final portion of our work to more carefully
handle a star's chemistry, we will modify DSEP to capture this variation in
convective efficiency.

### 2023-05-28 src/sections/fidanka.tex
Signifigant progress, wrote most of fidanka section

\section{fidanka}\label{sec:fidanka}
When fitting isochrones to the data we have four main critera for any method

\begin{itemize}
	\item The method must be robust enough to work along the entire main sequence, turn off, and much of the subgian and red giant branchs.
	\item Any method should consider photometric uncertanity in the fitting process.
	\item The method should be model independent, weighting any n number of populations equally.
	\item The method should be automated and require minimal intervention from the user.
\end{itemize}

While there are many packages which can measure fiducial lines very well
{\color{red}[CITATIONS]}, we do not belive that any of these perfectly match
our use case. Therefore, we elect to develope our own software suite,
\fidanka. \fidanka is a python package designed to automate
much of the process of measuring fiducual lines in CMDs, adhearing to the four
criteria we lay out above. Primary features of \fidanka may be seperated into
two categories: stellar population synthethis and isochrone
optimization/fitting (distance modulus, B-V color excess, and binpary mass
fraction)

\subsection{Fiducual Line Measurment}
\fidanka takes a interative approach to measuring fiducial lines, the first
step of which is to make a ``guess'' as to the fiducial line. This guess will
be used to verticalize the CMD so that further alorithms can work in 1-D
magnitude bins without worrying about weighting issues caused by varying
projections of the evolutionary sequence onto the magnitude axis. This initial
guess is calculated by splitting the CMD into magnitude bins, with uniform
numbers of stars per bin (so that bins are cover a small magnitude range over
densly populated regions of the CMD while covering a much larger mangnitude
range in sparsly populated regions of the CMD, such as the RGB). A unimodal
gaussian distribution is then fit to the color distribution of each bin, and
the resulting mean color is used as thec initial fiducial line guess. This
rough fiducual line will approximatly trace the area of highest density. We
subtract the color of this fiducual line from that of each star to verticalize
the CMD.

If \fidanka were to simply apply the same algorithm to the verticalized CMD
then the resulting fiducial line would simply be a re-extraction of the initial
fiducial line. To avoid this, we take a more robust, number density based
approach, which considers the distribution of stars in both color and magnitude
space simultaniously. For each star in the CMD we first using a
\texttt{introselect} partitioning algorithm to select the 50th nearest stars.
To account for the case where the star is at an extreme edge of the CMD, those
50 stars include the star itself (such that we really select 49 stars + 1). We
use \texttt{qhull}\footnote{https://www.qhull.com}\citep{Barber1996, } to
calculate the convex hull of those 50 points. The number density at each star
then is defined as 50/(area of convex hull). Because we use a fixed number of
points per star, and a partitioning algorithm as opposed to a sorting
algorithm, this method scales like $\mathcal{O}(n)$, where n is the number of
stars in the CMD. It also intrinsically weights the density of of each star
equally as the counting statistics of per convex are uniform. We are left with a
CMD where each star has a defined number density {\color{red}[FIGURE]}.

We can adapt this density map method to consider photometric uncertanties by
adopting a simple monte carlo approach. For each star in the CMD we draw a
random magnitude shift from a gaussian distribution with a standard deviation
equal to the photometric uncertanty of the star in each filter. We then shift
each star by this random amount and calculate the density map as before. We
repeat this process $m$ times, and then take the median density at each point
in the CMD {\color{red}[FIGURE]}. This method will result in noisy density
peaks with charectaristic width less than that of the photometric noise
smoothing out; while wider peaks will remain.

\fidanka can now exploit this density map to fit a better fiducual line to the
data, as the densiy map is far more robust to outlies. There are multiple
algorithms we impliment to fit the fiducial line to the color density profile
in each magnitude bin; they are explained in more detail in the \fidanka
documentation. However, of most relevance here is the A* path finding heuristic
over peaks. Peaks are extracted from the The color-density profile in at
density bin {\color{red}[FIGURE]}. The A* heuristic is then used to find an
optimal path (though not neccesarily {\em the} optimal path) through the peaks
{\color{red}[FIGURE]}. The resulting path is then used as the fiducial line
{\color{red}[FIGURE]}. The heursitc considers the slope of the path from one
bin to the next and simultaniously the change in density from one bin to the
next. This allows the path to be robust to both steep slopes and low density
regions. Due to the heuristic the fiducial line path  is not neccesarily the
vertical line defined by the initial fiducial line guess and will instead be a
more optimized/better guess.

This method of fiducial line extraction is very effective at tracing the
meandian ridge line of the overall CMD; however, it struggles to discriminate
between multiple populations. The density variations from one population to the
next are often too subtle. Moreover, when sampling the density. Moreover, the
spacing between main sequence populations may be of a similar order to the
photmetric uncertantities, and therefor the indivudual populations may smear
into one and other. For these reasons, \fidanka does not attempt to extract
multiple unique fiducuial lines for each population; instead, it measures the
width of the overall sequence. Width measurment again makes use of the
color-density pofile, selecting defining the width as the difference in color
between the 5th and 95th percentile of the density {\color{red}[FIGURE]}.

\subsection{Stellar Population Synthethis}
In addition to measuring fiducial lines, \fidanka also includes a stellar
population synthethis module. This module is used to generate synthetic CMDs
from a given set of isochrones. This is of primary importance for binary
population modelling. The module is also used to generate synthetic CMDs for
the purpose of testing the fiducial line extraction algorithms against priors.

\fidanka uses MIST formated isochrones {\color{red}[CITATION]} as input along
with distance modulus, B-V color excess, binary mass fraction, and bolometric
corrections. An arbitrarily large number of isochrones may be used to define an
arbitrary number of populations. Synthetic stars are samples from each
isochroner based on a definiable probability (for example it is belived that
$\sim90\%$ of stars in globular clusters are younger population
{\color{red}[CITATION]). Based on the metallicity, $\mu$, and E(B-V) of each
isochrone, bolometric corrections are taken from bolometric correction
tables. Where bolometric correction tables do not include exact metallicities
or extinctions a linear interpolation is preformed between the two bounding
values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
from a set of 2 NGC 2808 isochrones as well as a comparison between those isochrones and
the measured fiducual line of the synthetic population.

### 2023-05-28 src/sections/fidanka.tex
Transed-Name

@@
 {\color{red}[CITATIONS]}, we do not belive that any of these perfectly match
-our use case. Therefore, we elect to develope our own software suite,
-\fidanka. \fidanka is a python package designed to automate
-much of the process of measuring fiducual lines in CMDs, adhearing to the four
-criteria we lay out above. Primary features of \fidanka may be seperated into
-two categories: stellar population synthethis and isochrone
-optimization/fitting (distance modulus, B-V color excess, and binpary mass
-fraction)
+our use case. Therefore, we elect to develope our own software suite, \fidanka.
+\fidanka is a python package designed to automate much of the process of
+measuring fiducual lines in CMDs, adhearing to the four criteria we lay out
+above. Primary features of \fidanka may be seperated into three primary
+categories: fiducual line measurment, stellar population synthethis, and
+isochrone optimization/fitting. Additionally, there are utility functions which
+are detailed in the \fidanka documentation.
 
@@
 $\sim90\%$ of stars in globular clusters are younger population
-{\color{red}[CITATION]). Based on the metallicity, $\mu$, and E(B-V) of each
-isochrone, bolometric corrections are taken from bolometric correction
-tables. Where bolometric correction tables do not include exact metallicities
-or extinctions a linear interpolation is preformed between the two bounding
+{\color{red}[CITATION]}). Based on the metallicity, $\mu$, and E(B-V) of each
+isochrone, bolometric corrections are taken from bolometric correction tables.
+Where bolometric correction tables do not include exact metallicities or
+extinctions a linear interpolation is preformed between the two bounding
 values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
-from a set of 2 NGC 2808 isochrones as well as a comparison between those isochrones and
-the measured fiducual line of the synthetic population.
+from a set of 2 NGC 2808 isochrones as well as a comparison between those
+isochrones and the measured fiducual line of the synthetic population.
+
+\subsection{Isochrone Optimization}
+The optimization routines in \fidanka will find the best fit distance modulus,
+B-V color excess, and binary number fraction for a given set of isochrones. If
+a single isochrone is provided then the optimization is done by mimizing the
+$\chi^2$ of the perpendicular distnaces between an isochrone and a fiducual
+line. If multiple isochrones are provided then those isochrones are first used
+to run stellar population synthethis and generate a synthetic CMD. The
+optimization is then done by mimizing the $\chi^2$ of both the perpendicular
+distnaces between and widths of the observed fiducual line and the fiducual
+line of the synthetic CMD.

### 2023-06-30 src/ms.tex
Finished first pass introduction, split off some stuff into a modeling section
Signifigant progress, wrote most of fidanka section
Transed-Name
Paper updates

@@
 \newcommand\latex{La\TeX}
+\newcommand\fidanka{\texttt{Fidanka} }
 
@@
 
-\correspondingauthor{Thomas M. Boudreaux}
-\email{thomas.m.boudreaux.gr@dartmouth.edu, thomas@boudreauxmail.com}
+\correspondingauthor{Emily M. Boudreaux}
+\email{emily.m.boudreaux.gr@dartmouth.edu, emily@boudreauxmail.com}
 
-\author[0000-0002-2600-7513]{Thomas M. Boudreaux}
+\author[0000-0002-2600-7513]{Emily M. Boudreaux}
 \affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}
@@
 \author[0000-0003-3096-4161]{Brian C. Chaboyer}
+\affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}
+
+\author{Rehnata Hoh}
 \affiliation{Department of Physics and Astronomy, Dartmouth College, Hanover, NH 03755, USA}
@@
 \begin{abstract}
-	Over its approximately 100 year history stellar modeling has become an
-	essential tool for understanding certain astrophysical phenomena which are not
-	directly observable. Modeling allows for empirical constraints --- such as
-	elemental abundances, luminosities, and effective temperatures --- to strongly
-	inform non-observables such as a star's age, mass, and radius. Here we propose a
-	thesis in five parts, related through their use of both modeling and the
-	Dartmouth Stellar Evolution Program (DSEP) to conduct this modeling. In two of
-	the parts of this thesis we will use DSEP, in conjunction with atmospheric
-	boundary conditions generated by collaborators, to build chemically
-	self-consistent models of multiple populations (MPs) in the globular clusters
-	NGC 2808, 47 Tuc, and NGC 6752. We will infer helium abundances across MPs and
-	compare these inferred abundances to those from models which do not consider as
-	careful a handling of a star's chemistry. PLACEHOLDER
+	Globular Clusters (GCs) provide a unique astrophysical laboratory for
+	studying the formation and evolution of stars. GCs are old, dense, and it
+	has historically been believed that they have a single stellar population
+	(SSP, in some publications also simple stellar population). However, in the
+	last two decades, it has been definitively shown that most if not all Milky
+	Way GCs have multiple stellar populations (MPs). These MPs are chemically
+	distinct from one another, primarily separated by light element abundance
+	variations without the standard accompanying heavy element abundance
+	variations. In addition to the light element abundance variations, MPs also
+	have different inferred helium abundances. The origin of these MPs remains
+	an open question, and one which is sensitive to the population - population
+	compositional differences; consequently, the extent of the composition
+	variations is a key parameter to constrain. Metal abundances may be
+	directly measured spectroscopically; however, helium abundances are not
+	directly observable in GCs. Instead, helium abundances are inferred from
+	stellar models. It is therefore important to understand build stellar
+	models that are self-consistent in the compositions of the structure,
+	atmosphere, and opacity. In this work we present the first chemically
+	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808.
+	We find that the helium abundance of the second generation of stars is
+	higher than the first generation by {\color{red} SOME AMOUNT}.
+	{\color{blue} This is in agreement with previous studies of NGC 2808.}
 \end{abstract}
 
-\keywords{}
+\keywords{Globular Clusters (656), Stellar evolutionary models (2046)}
 
 \input{src/sections/intro.tex}
+
+\input{src/sections/AtmopshericModels.tex}
+
+\input{src/sections/modeling.tex}
+
+\input{src/sections/fidanka.tex}
+
+\input{src/sections/fitting.tex}
+
+\input{src/sections/results.tex}
+
+% \input{src/sections/discussion.tex}
+
+\input{src/sections/conclusion.tex}
 
@@
 	would like to thank Elisabeth Newton and Aaron Dotter for their support and
-	for useful disscusion related to the topic of this paper. We acknowledge
-	the support of a NASA grant (No. 80NSSC18K0634). 
+	for useful disscusion related to the topic of this paper. Additionally, we
+	would like to thank Kara Fagerstrom, Aylin Garcia Soto, and Keighley
+	Rockcliffe for their useful disscusion related to in this work. We
+	acknowledge the support of a NASA grant (No. 80NSSC18K0634). 
 \end{acknowledgments}

### 2023-06-30 src/sections/AtmopshericModels.tex
Paper updates

\section{Chemical Consistency}\label{sec:const}
There are three primary areas in which must the stellar models must be
consistent: the atmospheric boundary conditions, the opacities, and interior
abundances. The interior abundances are relatively easily handled by adjusting
parameters within our stellar evolutionary code. However, the other two areas are
more complicated to bring into consistency. Atmospheric boundary conditions and
opacities must both be calculated with a consistent set of chemical abundances
outside of DSEP. The

\subsection{Atmospheric Boundary Conditions}\label{sec:atm}
Certain assumptions {\color{red}[WHICH ONES,CITATION]} made in stellar structure
codes, such as DSEP, are valid when the optical depth of a star is small.
However, in the atmospheres of stars, the number density of particles drops low
enough and the optical depth consequently becomes large enough that these
assumptions break down, and more separate plasma modeling code is required.
Generally structure code will use tabulated atmospheric boundary conditions
generated by these specialized codes {\color{red} PHEONIX, ATLAS, MARCS +
[CITATIONS]}. Often, as the boundary conditions are both expensive to compute
and not the speciality of stellar structure researchers, the boundary
conditions are not updated as as light-element interior abundance varies.

One key element when chemically consistently modeling NGC 2808 modeling is the
incorporation of new atmospheric models with the same elemental abundances as
the structure code. We use atmospheres generated from the \texttt{MARCS} grid of
model atmospheres \citep{Plez2008}. \texttt{MARCS} provides one-dimensional,
hydrostatic, plane-parallel and spherical LTE atmospheric models
\citep{Gustafsson2008}. Model atmospheres are made to match the
spectroscopically measured elemental abundances of populations A and E.
Moreover, for each populations, atmospheres with  various helium mass fractions
are generated. These range from Y=0.24 to Y=0.36 in steps of 0.02. A comparison
of the pressure and temperature throughout the atmospheres of the two
populations with helium abundances representative of literature values is shown
in Figure \ref{fig:AEAtmComp}.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{src/figures/notebookFigures/AtmosphereComparison.pdf}
	\label{fig:AEAtmComp}
	\caption{Comparison of the MARCS model atmospheres generated for the two
	extreme populations of NGC 2808. These lines shows population A and E with
	the same Helium abundance; though, we fit a grid of models over various
	helumn abundances. Dashed lines show the temperature of the boundary
	condition while sold lines show the pressure.}
\end{figure}

\subsection{Opacities}\label{sec:opac}
In addition to the atmospheric boundary conditions, both the high and low
temperature opacities used by DSEP must be made chemically consistent. Here we
use OPLIB high temperature opacity tables \citep{Colgan2016} retrieved using
the TOPS web-interface. Low temperature opacity tables are retrieved from the
Aesopus 2.0 web-interface \citep{Marigo2009, Marigo2022}. Ideally, these
opacities would be the same used in the atmospheric models. However, the
opacities used in the MARCS models are not publicly available. As such, we use
the opacities provided by the TOPS and Aesopus 2.0 web-interfaces.

### 2023-06-30 src/sections/fidanka.tex
Paper updates

--- 2023-05-28 src/sections/fidanka.tex
@@
 \section{fidanka}\label{sec:fidanka}
-When fitting isochrones to the data we have four main critera for any method
+When fitting isochrones to the data we have four main criteria for any method
 
 \begin{itemize}
-	\item The method must be robust enough to work along the entire main sequence, turn off, and much of the subgian and red giant branchs.
-	\item Any method should consider photometric uncertanity in the fitting process.
+	\item The method must be robust enough to work along the entire main sequence, turn off, and much of the subgiant and red giant branchs.
+	\item Any method should consider photometric uncertainty in the fitting process.
 	\item The method should be model independent, weighting any n number of populations equally.
@@
 
-While there are many packages which can measure fiducial lines very well
-{\color{red}[CITATIONS]}, we do not belive that any of these perfectly match
-our use case. Therefore, we elect to develope our own software suite,
-\fidanka. \fidanka is a python package designed to automate
-much of the process of measuring fiducual lines in CMDs, adhearing to the four
-criteria we lay out above. Primary features of \fidanka may be seperated into
-two categories: stellar population synthethis and isochrone
-optimization/fitting (distance modulus, B-V color excess, and binpary mass
-fraction)
+We do not believe that any currently available software is a match for
+our use case. Therefore, we elect to develop our own software suite, \fidanka.
+\fidanka is a python package designed to automate much of the process of
+measuring fiducial lines in CMDs, adhering to the four criteria we lay out
+above. Primary features of \fidanka may be separated into three primary
+categories: fiducial line measurement, stellar population synthesise, and
+isochrone optimization/fitting. Additionally, there are utility functions which
+are detailed in the \fidanka documentation.
 
-\subsection{Fiducual Line Measurment}
-\fidanka takes a interative approach to measuring fiducial lines, the first
-step of which is to make a ``guess'' as to the fiducial line. This guess will
-be used to verticalize the CMD so that further alorithms can work in 1-D
-magnitude bins without worrying about weighting issues caused by varying
-projections of the evolutionary sequence onto the magnitude axis. This initial
-guess is calculated by splitting the CMD into magnitude bins, with uniform
-numbers of stars per bin (so that bins are cover a small magnitude range over
-densly populated regions of the CMD while covering a much larger mangnitude
-range in sparsly populated regions of the CMD, such as the RGB). A unimodal
-gaussian distribution is then fit to the color distribution of each bin, and
-the resulting mean color is used as thec initial fiducial line guess. This
-rough fiducual line will approximatly trace the area of highest density. We
-subtract the color of this fiducual line from that of each star to verticalize
-the CMD.
+\subsection{Fiducial Line Measurement}
+\fidanka takes a iterative approach to measuring fiducial lines, the first step
+of which is to make a ``guess'' as to the fiducial line. . This initial guess
+is calculated by splitting the CMD into magnitude bins, with uniform numbers of
+stars per bin (so that bins are cover a small magnitude range over densely
+populated regions of the CMD while covering a much larger magnitude range in
+sparsely populated regions of the CMD, such as the RGB). A unimodal Gaussian
+distribution is then fit to the color distribution of each bin, and the
+resulting mean color is used as the initial fiducial line guess. This rough
+fiducial line will approximately trace the area of highest density. The initial
+guess will be used to verticalze the CMD so that further algorithms can work in
+1-D magnitude bins without worrying about weighting issues caused by varying
+projections of the evolutionary sequence onto the magnitude axis.
+Verticalization is preformed taking the difference between the guess fiducial
+line and the color of each star in the CMD.
 
 If \fidanka were to simply apply the same algorithm to the verticalized CMD
-then the resulting fiducial line would simply be a re-extraction of the initial
-fiducial line. To avoid this, we take a more robust, number density based
+then the resulting fiducial line would likely be a re-extraction of the initial
+fiducial line guess. To avoid this, we take a more robust, number density based
 approach, which considers the distribution of stars in both color and magnitude
-space simultaniously. For each star in the CMD we first using a
+space simultaneously. For each star in the CMD we first using a
 \texttt{introselect} partitioning algorithm to select the 50th nearest stars.
@@
 calculate the convex hull of those 50 points. The number density at each star
-then is defined as 50/(area of convex hull). Because we use a fixed number of
-points per star, and a partitioning algorithm as opposed to a sorting
-algorithm, this method scales like $\mathcal{O}(n)$, where n is the number of
-stars in the CMD. It also intrinsically weights the density of of each star
-equally as the counting statistics of per convex are uniform. We are left with a
-CMD where each star has a defined number density {\color{red}[FIGURE]}.
+then is defined as $50/A_{hull}$, where $A_{hull}$ is the area of the convex
+hull. Because we use a fixed number of points per star, and a partitioning
+algorithm as opposed to a sorting algorithm, this method scales like
+$\mathcal{O}(n)$, where n is the number of stars in the CMD. This method also
+intrinsically weights the density of of each star equally as the counting
+statistics per bin are uniform. We are left with a CMD where each star
+has a defined number density (Figure \ref{fig:densityMapDemo}).
 
-We can adapt this density map method to consider photometric uncertanties by
-adopting a simple monte carlo approach. For each star in the CMD we draw a
-random magnitude shift from a gaussian distribution with a standard deviation
-equal to the photometric uncertanty of the star in each filter. We then shift
-each star by this random amount and calculate the density map as before. We
-repeat this process $m$ times, and then take the median density at each point
-in the CMD {\color{red}[FIGURE]}. This method will result in noisy density
-peaks with charectaristic width less than that of the photometric noise
-smoothing out; while wider peaks will remain.
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.9\textwidth]{src/figures/notebookFigures/DensityMapDemo.png}
+	\label{fig:densityMapDemo}
+	\caption{Density map demo showing density estimate over different parts of
+	the evolutionary sequence. The left panel shows the density map over the
+	entire evolutionary sequence, while the middle panel shows the density map
+	over the main sequence and the right most panel shows the density map over
+	the RGB. Figures in the top row are the raw CMD, while figures in the
+	bottom row are colored by the density map.}
+\end{figure*}
 
-\fidanka can now exploit this density map to fit a better fiducual line to the
-data, as the densiy map is far more robust to outlies. There are multiple
-algorithms we impliment to fit the fiducial line to the color density profile
-in each magnitude bin; they are explained in more detail in the \fidanka
-documentation. However, of most relevance here is the A* path finding heuristic
-over peaks. Peaks are extracted from the The color-density profile in at
-density bin {\color{red}[FIGURE]}. The A* heuristic is then used to find an
-optimal path (though not neccesarily {\em the} optimal path) through the peaks
-{\color{red}[FIGURE]}. The resulting path is then used as the fiducial line
-{\color{red}[FIGURE]}. The heursitc considers the slope of the path from one
-bin to the next and simultaniously the change in density from one bin to the
-next. This allows the path to be robust to both steep slopes and low density
-regions. Due to the heuristic the fiducial line path  is not neccesarily the
-vertical line defined by the initial fiducial line guess and will instead be a
-more optimized/better guess.
+\fidanka can now exploit this density map to fit a better fiducial line to the
+data, as the density map is far more robust to outliers. There are multiple
+algorithms we implement to fit the fiducial line to the color-density profile
+in each magnitude bin (Figure \ref{fig:densityBinsDemo}); they are explained in more detail in the \fidanka
+documentation. However, of most relevance here is the Bayesian Gaussian Mixture
+Modeling (BGMM) method. BGMM is a clustering algorithm which, for some fixed
+number of n-dimensional Gaussian distributions, $K$, determines the mean, covariance, and
+mixing probability (somewhat analogous to amplitude) of each $k^{th}$
+distribution, such that the local lower bound of the evidence of each star
+belonging strongly to a single distribution is maximized.
 
-This method of fiducial line extraction is very effective at tracing the
-meandian ridge line of the overall CMD; however, it struggles to discriminate
-between multiple populations. The density variations from one population to the
-next are often too subtle. Moreover, when sampling the density. Moreover, the
-spacing between main sequence populations may be of a similar order to the
-photmetric uncertantities, and therefor the indivudual populations may smear
-into one and other. For these reasons, \fidanka does not attempt to extract
-multiple unique fiducuial lines for each population; instead, it measures the
-width of the overall sequence. Width measurment again makes use of the
-color-density pofile, selecting defining the width as the difference in color
-between the 5th and 95th percentile of the density {\color{red}[FIGURE]}.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{src/figures/notebookFigures/DensityBinsDemo.png}
+	\label{fig:densityBinsDemo}
+	\caption{CMD where points are colored by density. Lines show the
+	density-color profile in each magnitude bin. In this figure adaptive
+	binning targeted 1000 stars per bin}
+\end{figure}
 
-\subsection{Stellar Population Synthethis}
+Maximization is preformed using the Dirichlet process, which is a
+non-parametric Bayesian method of determining the number of Gaussian distributions, $K$,
+which best fit the data {\color{red}[CITATION]}. Use of the Dirichlet process
+allows for dynamic variation in the number of inferred populations from
+magnitude bin to magnitude bin. Specifically, populations are clearly visually
+separated from the lower main sequence through the turn off; however, at the
+turn off and throughout much of the subgiant branch, the two visible
+populations overlap due to their extremely similar ages ({\color{red}
+Citation}). The Dirichlet process allows for the BGMM method to infer a single
+population in these regions, while inferring two populations in regions where
+they are clearly separated. More generally, the use of the Dirichlet process
+removes the need for a prior on the exact number of populations to fit. Rather,
+the user specifies a upper bound on the number of populations within the
+cluster. An example bin (F814W = 20.6) is shown in Figure \ref{fig:BGMMDist}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.9\textwidth]{Notebooks/Figures/BGMMMixingBin.pdf}
+	\caption{Example of BGMM fit to a magnitude bin. The grey line shows the
+	underlying color-density profile, while the black dashed-line shows the
+	joint distribution of each BGMM component. The solid black lines show the
+	two selected components.}
+	\label{fig:BGMMDist}
+\end{figure*}
+
+\fidanka's BGMM method first breaks down the verticalized CMD into magnitude
+bins with uniform numbers of stars per bin (here we adopt 250). Any stars left
+over are placed into the final bin. For each bin a BGMM model with a maximum of
+5 populations is fit to the color density profile. The number of populations is
+then inferred from the weighting parameter (the mixing probability) of each
+population. If the weighting parameter of any $k^{th}$ components less than
+{\color{blue}0.05}, then that component is considered to be spurious and
+removed. Additionally, if the number of populations in the bin above and the
+bin below are the same, then the number of populations in the current bin is
+forced to be the same as the number of populations in the bin above. Finally,
+the initial guess fiducial line is added back to the BGMM inferred line. Figure
+\ref{fig:vertFit} shows the resulting fiducial line(s) in each magnitude bin
+for both a verticalized CMD and a non verticalized CMD.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{Notebooks/Figures/vertFit.png}
+	\caption{CMD where points are colored by density. Line trace the infered 
+	fiducial line(s) in each magnitude bin.}
+	\label{fig:vertFit}
+\end{figure}
+
+This method of fiducial line extraction effectively discriminated between
+multiple populations long the main sequence and RGB of a cluster, while
+simultaneously allowing for the presence of a single population along the MSTO
+and subgiant branch.
+
+We can adapt this density map based BGMM method to consider photometric
+uncertainties by adopting a simple Monte Carlo approach. Instead of measuring
+the fiducial line(s) a single time, \fidanka can measure the fiducial line(s)
+many times, resampling the data with replacement each time. For each resampling
+\fidanka adds a random offset to each filter based on the photometric
+uncertainties of each star. From these $n$ measurments the mean fiducial line
+for each sequence can be identified along with upper and lower bound confidence
+intervals in each magnitude bin.
+
+\subsection{Stellar Population Synthesis}
 In addition to measuring fiducial lines, \fidanka also includes a stellar
-population synthethis module. This module is used to generate synthetic CMDs
+population synthesise module. This module is used to generate synthetic CMDs
 from a given set of isochrones. This is of primary importance for binary
@@
 
-\fidanka uses MIST formated isochrones {\color{red}[CITATION]} as input along
+\fidanka uses MIST formatted isochrones {\color{red}[CITATION]} as input along
 with distance modulus, B-V color excess, binary mass fraction, and bolometric
@@
 arbitrary number of populations. Synthetic stars are samples from each
-isochroner based on a definiable probability (for example it is belived that
+isochrone based on a definable probability (for example it is believed that
 $\sim90\%$ of stars in globular clusters are younger population
-{\color{red}[CITATION]). Based on the metallicity, $\mu$, and E(B-V) of each
-isochrone, bolometric corrections are taken from bolometric correction
-tables. Where bolometric correction tables do not include exact metallicities
-or extinctions a linear interpolation is preformed between the two bounding
+{\color{red}[CITATION]}). Based on the metallicity, $\mu$, and E(B-V) of each
+isochrone, bolometric corrections are taken from bolometric correction tables.
+Where bolometric correction tables do not include exact metallicities or
+extinctions a linear interpolation is preformed between the two bounding
 values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
-from a set of 2 NGC 2808 isochrones as well as a comparison between those isochrones and
-the measured fiducual line of the synthetic population.
+from a set of 2 NGC 2808 isochrones as well as a comparison between those
+isochrones and the measured fiducial line of the synthetic population.
+
+\subsection{Isochrone Optimization}
+The optimization routines in \fidanka will find the best fit distance modulus,
+B-V color excess, and binary number fraction for a given set of isochrones. If
+a single isochrone is provided then the optimization is done by minimizing the
+$\chi^2$ of the perpendicular distances between an isochrone and a fiducial
+line. If multiple isochrones are provided then those isochrones are first used
+to run stellar population synthesis and generate a synthetic CMD. The
+optimization is then done by minimizing the $\chi^2$ of both the perpendicular
+distances between and widths of the observed fiducial line and the fiducial
+line of the synthetic CMD.
+
+\subsection{Fidanka Testing}
+In order to validate fidanka we have run a series of tests on synthetic CMDs
+generated from NGC 2808 isochrones. For each test we use fidanka to both build
+a synthetic population and then measure the fiducial line of that population.
+The measured fiducial lines(s) are then compared to the underlying isochrones
+used.

### 2023-06-30 src/sections/fitting.tex
Paper updates

\section{Isochrone Fitting}\label{sec:isoFit}
We fit pairs of isochrones to the HUGS data for NGC 2808 using \fidanka, as
descrbed in \S {\color{red}FIDANKA SECTION}. Two isochrones, one for Population
A and one for Population E are fit simultaneously. These isochrones are
constrained to have the same distance modulus, $\mu$, and color excess, E(B-V).
Moreover, we constrain the mixing length, $\alpha_{ML}$, to be constant between
any two isochrones in a set. For every isochrone in the set of combination of
which fulfilling these constraints $\mu$, $E(B-V)$, Age$_{A}$, and $Age_{B}$
are optimized to reduce the $\chi^{2}$ distance between the fiducial
line{\color{red}s} and the isochrones. Because we fit fiducial lines directly,
we do not need to consider the binary population fraction, $f_{bin}$, as a free
parameter.

{\color{red}Table \ref{tab:isoFit}} shows the results of the isochrone fitting
for NGC 2808. The best fit isochrones are shown in {\color{red}Figure
\ref{fig:isoFit}.}

{\color{red} Disscus the implications of the specific isochrones we fit.}

\subsection{ACS-HUGS Photometric Zero Point Offset}
The Hubble legacy archive photometry used in this work is calibrated to the
Vega magnitude system. However, we have found that the photometry has a
systematic offset of {\color{red}$\sim0.02$ magnitudes} in the F814W band when
compared to the same stars in the ACS survey {\color{red} [CITATION]}. The
exact cause of this offset is unknown, but it is likely due to a difference in
the photometric zero point between the two surveys. A full correction of this
offset would require a careful re-reduction of the HUGS photometry, which is
beyond the scope of this work. We instead recognize a 0.02 inherent uncertainty
in the inferred magnitude of any fit when comparing to the ACS survey. This
uncertainty is {\color{red} small when compared to the uncertainty in the
distance modulus and should not affect the conclusion of this
paper}.

{\color{red} Figure Showing the offset}

{\color{blue}The independent analysis of the Hubble Space Telescope photometry
ACS and HUGS, and an additional ground-based dataset created by Stetson et al.
(2009), of the globular cluster NGC2808 resulted in findings of a systematic
difference in the magnitude of the stars. A significant offset between the
three datasets was found. HUGS and ACS were found to have consistent data for
Vvega, however an offset of approximately 0.025 was found in the Ivega. ACS and
Stetson were found to have inconsistent differences in both Vvega and Ivega.
The three photometric studies do not match, and future studies which compare
theoretical models to the data will need to take into account these systematic
uncertainties. }

### 2023-06-30 src/sections/intro.tex
Paper updates

@@
 \section{Introduction}\label{sec:Intro}
-Globular clusters (GCs) are among the oldest observ- able objects in the
+Globular clusters (GCs) are among the oldest observable objects in the
 universe \citep{Pen11}. They are characterized by high densities with typical
@@
 ranging from $10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs
-are signifigantly larger than these typical values {\color{red}EXAMPLE}. GCs
+are significantly larger than these typical values {\color{red}EXAMPLE}. GCs
 provide a unique way to probe stellar evolution \citep{Bau03}, galaxy formation
-models \citep{Boy18,Kra05}, and dark matter halo struc- ture \citep{Hud18}.
+models \citep{Boy18,Kra05}, and dark matter halo structure \citep{Hud18}.
 {\color{red} BRING IN SOME MORE RECENT CITATIONS.}
 
-Whereas, people have have often tried to categorized objects as GCs through
-relations between half-light radius, density, and surface brightness profile,
-in fact many objects which are generally thought of as GCs don't cleanly fit
-into these cuts {\color{red} EXAMPLE + CITATION}. Consequently,
-\citet{Carretta2010} proposed a definition of GC based on observed chemical
-inhomogeneities in their stellar populations. The modern understanding of GCs
-then is not simply one of a dense cluster of stars which may have chemical
-inhomogeneities and multiple populations; rather, it is one where those
-chemical inhomogeneities and multiple populations themselves are the defining
-element of a GC.
+The traditional view of Globular Clusters was, for a long time, that they
+consisted of a single stellar population (SSP, in some publications this is
+referred to as a Simple Stellar Population). This view was supported by
+spectroscopically uniform heavy element abundances \citep{Carretta2009}
+{\color{red}[CHECK]}, and the lack of evidence for multiple stellar populations
+(MPs) in the color-magnitude diagrams of GCs \citep{Milone2017}. However, in
+the last two decades, it has been definitively shown that most if not all Milky
+Way GCs have MPs \citep{Piotto2015}. The lack of photometric evidence for MPs
+can be attributed to the short color throw available to ground based
+photometric surveys \citep{Milone20Here17}. While MPs are chemically distinct
+from one another, that distinction is most prominent when observing with $U$
+and $B$ filters \citep{Sbordone2011}.
+
+The prevalence of multiple populations in GCs is so distinct that the proposed
+definitions for what constitutes a globular cluster now often center the
+existence of MPs. Whereas, people have have often tried to categorized objects
+as GCs through relations between half-light radius, density, and surface
+brightness profile, in fact many objects which are generally thought of as GCs
+don't cleanly fit into these cuts {\color{red} EXAMPLE + CITATION}.
+Consequently, \citet{Carretta2010} proposed a definition of GC based on
+observed chemical inhomogeneities in their stellar populations. The modern
+understanding of GCs then is not simply one of a dense cluster of stars which
+may have chemical inhomogeneities and multiple populations; rather, it is one
+where those chemical inhomogeneities and multiple populations themselves are
+the defining element of a GC.
 
@@
 \citep[FRMSs,][]{Decressin2007}, super massive stars
-\citep[SMSs,][]{Denissenkov2014}, and massive interacing binaries
+\citep[SMSs,][]{Denissenkov2014}, and massive interacting binaries
 \citep[MIBs,][]{deMink2009, Bastian2018}.
@@
 severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
-models require signifigant mass loss ($\sim 90\%$) between cluster formation
-and the current epoch --- implying that a signifigant fraction of halo stars
+models require significant mass loss ($\sim 90\%$) between cluster formation
+and the current epoch --- implying that a significant fraction of halo stars
 formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.
@@
 In addition to the light-element anti-correlations observed it is also known
-that younger populations are signifigantly enhanced in Helium
+that younger populations are significantly enhanced in Helium
 \citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
@@
 GCs have yet been studied with chemically self-consistent (structure and
-atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}. Here we present new,
-chemically self-consistent modeling og the two extreme populations of NGC 2808
-identified by \citet{Milone2015}, A and E.
+atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.
+
+{\color{blue} NGC 2808 is the prototype globular cluster to host Multiple
+Populations.} Various studies since 2007 have identified that it may host
+anywhere from 2-5 stellar populations. These populations have been identified
+both spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}.
+Note that recent work \citep{Valle2022} calls into question the statistical significance
+of the detections of more than 2 populations in the spectroscopic data. Here we
+present new, chemically self-consistent modeling of the two extreme populations
+of NGC 2808 identified by \citet{Milone2015}, populations A and E.
+{\color{blue} Additionally, we present a likelihood analysis of the photometric
+data of NGC 2808 to determine the number of populations present in the cluster.}

### 2023-06-30 src/sections/modeling.tex
Paper updates

@@
-\section{Modeling}\label{sec:modeling}
-One key element of NGC 2808 modeling is the incorporation of new atmospheric
-models, generated from the \texttt{MARCS} grid of model atmospheres \citep{Plez2008},
-which match interior elemental abundances. \texttt{MARCS} provides one-dimensional,
-hydrostatic, plane-parallel and spherical LTE atmopsheric models
-\citep{Gustafsson2008}. Members of our collaboration have generated atmospheric 
-models for populations A and E.  Integration of these new model atmospheres
-into DSEP is ongoing.
+\section{Stellar Models}\label{sec:modeling}
+We use the Dartmouth Stellar Evolution Program \citep[DSEP, ][]{Dotter2008} to
+generate stellar models. DSEP is a well-tested, one-dimensional stellar
+evolution code which includes a mixing length model of convection,
+gravitational settling, and diffusion.
 
-For similar reasons as discussed in \S\ref{sec:p1} we conduct this research
-with OPLIB high-temperature opacity tables as opposed to OPAL tables. We will
-also generate low temperature opacity tables using the \texttt{MARCS}.
-Moreover, we confirm that the atmosphere and structure meet in an optically
-thick region of the star by shifting the atmospheric fitting point from an optical
-depth of $\tau = 2/3$ (used by DSEP currently for \texttt{PHOENIX} model atmospheres) to
-some higher $\tau$. We will experiment to identify the best optical depth to
-fit at..
+We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
+masses from the zero-age main sequence (ZAMS) to the tip of the red giant
+branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
+above 0.7 $M_{\odot}$ we evolve a model every 0.5 $M_{\odot}$. Additionally, we
+evolve models over a grid of mixing length parameters, $\alpha_{MLT}$, from
+$\alpha_{MLT} = 1.0$ to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the
+mixing length grid the evolved grid of models also has dimensions population (A
+or E) and helium abundance ($Y$). Each model is evolved in DSEP's ``high
+resolution'' mode and had a maximum allowed time step of 50 Myr.
 
-These population have been studied in depth by Feiden and their chemical
-compositions were determined in \citet{Milone2015} (see Table 2 in that paper).
-While we cannot yet evolve DSEP models with these new boundary conditions, we
-can make a first pass investigation of the affect of OPLIB opacities (Figure
-\ref{fig:NGC2808ISO}). Note how the models generated using OPLIB opacity tables
-have a systematically lower luminosity. This discrepancy is consistent with
-the overall lower opacities of the OPLIB tables.
-
-The isochrones generally used to infer the degree of helium enhancements assume that
-convection operates in the same manner in metal-poor stars as it does in the
-Sun. However, observations from \textit{Kepler} of metal-poor red giants
-\citep{Bonaca2012, tayar2017correlation}, in concert with interferometric
-radius determination of the metal-poor sub-giant HD 140283
-\citep{creevey2015benchmark}, have shown that the efficiency of convection
-changes with iron content. As the final portion of our work to more carefully
-handle a star's chemistry, we will modify DSEP to capture this variation in
-convective efficiency.
+For each combination of population, $Y$, and $\alpha_{MLT}$ we use the
+isochrone generation code first presented in \citet{Dotter2016} to generate a
+grid of isochrones. The isochrone generation code identified equivalent
+evolutionary points (EEPs) over a series of masses and interpolates between
+them. {\color{blue} The grid of isochrones generated for this work is avalible
+as a digital supplement to this paper.}

### 2023-06-30 src/sections/results.tex
Paper updates

\section{Results}\label{sec:results}
Using \fidanka we fit pairs of Population A + E isochrones to the HUGS data for
NGC 2808. Each pair of isochrones is allowed to vary in distance modulus,
reddening, relative helium mass fraction (A/E), and age. The $\chi^{2}$
distribution for the isochrone pairs is shown in Figure {\color{red}[FIGURE]}.
The best fit isochrones are shown in Figure {\color{red}[FIGURE]} and optimized
parameters for these are presented in Table {\color{red}[TABLE]}.

### 2023-07-21 src/ms.tex
Updated paper

@@
 	studying the formation and evolution of stars. GCs are old, dense, and it
-	has historically been believed that they have a single stellar population
-	(SSP, in some publications also simple stellar population). However, in the
+	has historically been believed that they have a single stellar population. However, in the
 	last two decades, it has been definitively shown that most if not all Milky
 	Way GCs have multiple stellar populations (MPs). These MPs are chemically
-	distinct from one another, primarily separated by light element abundance
+	distinct from one another, primarily separated by light element, including helium, abundance
 	variations without the standard accompanying heavy element abundance
-	variations. In addition to the light element abundance variations, MPs also
-	have different inferred helium abundances. The origin of these MPs remains
+	variations. As the precise formation channel of these MPs remains
 	an open question, and one which is sensitive to the population - population
-	compositional differences; consequently, the extent of the composition
-	variations is a key parameter to constrain. Metal abundances may be
+	compositional differences, the extent of the composition
+	variations between MPs is a key parameter to constrain. Many metal abundances may be
 	directly measured spectroscopically; however, helium abundances are not
@@
 	atmosphere, and opacity. In this work we present the first chemically
-	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808.
+	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative opacities, and AESOPUS low-temperature radiative opacities.
 	We find that the helium abundance of the second generation of stars is

### 2023-07-21 src/sections/AtmopshericModels.tex
Updated paper

@@
 \section{Chemical Consistency}\label{sec:const}
-There are three primary areas in which must the stellar models must be
+There are three primary areas in which must the stellar models must be made chemically
 consistent: the atmospheric boundary conditions, the opacities, and interior
@@
 opacities must both be calculated with a consistent set of chemical abundances
-outside of DSEP. The
+outside of the stellar evolution code.
+For evolution we use the Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008}, a well tested 1D stellar evolution code which has a particular focus on modelling low mass stars ($\le 2$ M$_{\odot}$)
 
 \subsection{Atmospheric Boundary Conditions}\label{sec:atm}
-Certain assumptions {\color{red}[WHICH ONES,CITATION]} made in stellar structure
+Certain assumptions, primarily that the radiation field is at equilibirum and radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
 codes, such as DSEP, are valid when the optical depth of a star is small.
@@
 enough and the optical depth consequently becomes large enough that these
-assumptions break down, and more separate plasma modeling code is required.
+assumptions break down, and separate, more physically motivated, plasma modeling code is required.
 Generally structure code will use tabulated atmospheric boundary conditions
-generated by these specialized codes {\color{red} PHEONIX, ATLAS, MARCS +
-[CITATIONS]}. Often, as the boundary conditions are both expensive to compute
+generated by these specialized codes ATLAS9 \citep{Kurucz1993}, PHEONIX \citep{Husser2013}, MARCS \citep{Gustafsson2008}, and MPS-ATLAS \citep{Kostogryz2023}.
+Often, as the boundary conditions are both expensive to compute
 and not the speciality of stellar structure researchers, the boundary

### 2023-07-21 src/sections/fidanka.tex
Started working on the fidanka testing section

@@
 \subsection{Fidanka Testing}
-In order to validate fidanka we have run a series of tests on synthetic CMDs
-generated from NGC 2808 isochrones. For each test we use fidanka to both build
-a synthetic population and then measure the fiducial line of that population.
-The measured fiducial lines(s) are then compared to the underlying isochrones
-used.
+In order to validate fidanka we have run an series of injection recovery tests
+using \fidanka's population synthesis routines to build various synthetic
+populations and \fidanka's fiducial measurement routines to recover these
+populations. We run multiple tests in order to validate \fidanka's ability to
+extract varying numbers of populations without the prior of the exact population
+number. Table \ref{tab:fidankaTests} provides the parameters for each injection recovery
+test along with the $\chi^{2}$ difference between each isochrone and its associated fiducial line.

### 2023-07-21 src/sections/intro.tex

@@
 of the detections of more than 2 populations in the spectroscopic data. Here we
-present new, chemically self-consistent modeling of the two extreme populations
+present new, chemically self-consistent modeling of the photometry of the two extreme populations
 of NGC 2808 identified by \citet{Milone2015}, populations A and E.

### 2023-07-21 src/sections/fidanka.tex
Major progress on injection recovery test section

@@
 test along with the $\chi^{2}$ difference between each isochrone and its associated fiducial line.
+
+Each population was generated using either a salpeter initial mass function \citep{Salpeter1955} or the initial mass function given in \citep{Milone2012} ($\alpha=-1.2$ redmost population and $\alpha=-0.9$ for the bluemost and second bluemost populations).
+Every population was assumed to have a binary population fraction of 10\%, to have a distance of 0pc and to have a B-V color excess of 0.
+Finally, each synthetic population was generated using a fixedf age of 12 Gyr.
+
+\begin{table}
+\end{table}
+
+The top panel Figure \ref{} shows the populations generated for these tests. while the bottom panel shows the populations with the density variations highlighted.
+
+We measure the fiducial lines in these populations using \fidanka's fiducial measurment utility. For the same
+reasons as outlines in Section \ref{} we use the F275W and F814W filters.
+A maximum population number is set at 5 for each trial.
+Figure \ref{} shows the fiducual lines on top of each synthethic population.
+Recall from Section \ref{} that use of Baysian Gaussian Mixture Modeling (BGMM) allows us to predict the optimal number of populations to recreate a distribution; therefore, where you see a single line BGMM has predicted only one population is needed whereas when you see 2 lines BGMM has preicted that 2 populations are needed.
+Importantly, these population numbers are not hard coded into our injection and recovery tests.
+
+The efficacy of the fiducual measurment it evaluated by calculating the $\chi^{2}$ metric between the fiducial line and isochrone over 0.1 mag bins.
+This allows us to probe which portions of the evolutionary sequence contribute most to the overall $\chi^{2}$ difference (Figure \ref{}).

### 2023-07-21 src/sections/results.tex
Added some more placeholder sections

@@
 NGC 2808. Each pair of isochrones is allowed to vary in distance modulus,
-reddening, relative helium mass fraction (A/E), and age. The $\chi^{2}$
+reddening, relative helium mass fraction (A/E), and age. Any population pairs which vary by more than 1\% in distance modulus or B-V color excess are rejected. The $\chi^{2}$
 distribution for the isochrone pairs is shown in Figure {\color{red}[FIGURE]}.
-The best fit isochrones are shown in Figure {\color{red}[FIGURE]} and optimized
+The best fit isochrones are shown in Figure \ref{fig:BestFitResults} and optimized
 parameters for these are presented in Table {\color{red}[TABLE]}.
+
+{\color{red} Need to make the chi2 dist plot still. Have all these values but need to figure out best way to visualize it}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/BestFit.png}
+  \label{fig:BestFitResults}
+  \caption{Best fit isochrone results for NGC 2808.}
+\end{figure}
+
+{\color{blue} Currently are still seeing a discontinutiy in the isochrobne below the MSTO. This must be addressed before submission.}

### 2023-09-01 src/sections/fidanka.tex
Updated with actual results finally

@@
 measuring fiducial lines in CMDs, adhering to the four criteria we lay out
-above. Primary features of \fidanka may be separated into three primary
+above. Primary features of \fidanka may be separated into three
 categories: fiducial line measurement, stellar population synthesise, and
@@
 non-parametric Bayesian method of determining the number of Gaussian distributions, $K$,
-which best fit the data {\color{red}[CITATION]}. Use of the Dirichlet process
+which best fit the data \citep{Ferguson1973, scikit-learn}. Use of the Dirichlet process
 allows for dynamic variation in the number of inferred populations from
@@
 turn off and throughout much of the subgiant branch, the two visible
-populations overlap due to their extremely similar ages ({\color{red}
-Citation}). The Dirichlet process allows for the BGMM method to infer a single
+populations overlap due to their extremely similar ages \citep[i.e.][]{Jordan2002}. The Dirichlet process allows for the BGMM method to infer a single
 population in these regions, while inferring two populations in regions where
@@
 
-\fidanka uses MIST formatted isochrones {\color{red}[CITATION]} as input along
+\fidanka uses MIST formatted isochrones \citep{Dotter2016} as input along
 with distance modulus, B-V color excess, binary mass fraction, and bolometric

### 2023-09-01 src/sections/fitting.tex
Updated with actual results finally

@@
 A and one for Population E are fit simultaneously. These isochrones are
-constrained to have the same distance modulus, $\mu$, and color excess, E(B-V).
+constrained to have distance modulus, $\mu$, and color excess, E(B-V) which agree to within 1\%.
 Moreover, we constrain the mixing length, $\alpha_{ML}$, to be constant between
@@
 are optimized to reduce the $\chi^{2}$ distance between the fiducial
-line{\color{red}s} and the isochrones. Because we fit fiducial lines directly,
+lines and the isochrones. Because we fit fiducial lines directly,
 we do not need to consider the binary population fraction, $f_{bin}$, as a free
@@
 
-{\color{red}Table \ref{tab:isoFit}} shows the results of the isochrone fitting
-for NGC 2808. The best fit isochrones are shown in {\color{red}Figure
-\ref{fig:isoFit}.}
+The best fit isochrones are shown in Figure \ref{fig:BestFitResults} and optimized
+parameters for these are presented in Table \ref{tab:BestFitResults}.
+We find helium mas fractions which are consistent with those identified in past literature \citep[e.g.][]{Milone2015}.
+Note that our helium mass fraction gird has a spacing of 0.03 between grid points and we are therefore unable to resolve between certain proposed helium mass fractions for the younger sequence (for example between 0.37 and 0.39).
 
-{\color{red} Disscus the implications of the specific isochrones we fit.}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/BestFitResults.pdf}
+  \label{fig:BestFitResults}
+  \caption{Best fit isochrone results for NGC 2808.}
+\end{figure}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{c | c c c c c c}
+    \hline
+    population & age & distance modulus & extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
+    & [Gyr] & & [mag] & & &\\
+    \hline
+    \hline
+    A & 12.3 & 14.91 & 0.54 & 0.24 & 1.901 & 0.014\\
+    E & 14.3 & 14.96 & 0.54 & 0.39 & 1.750 & 0.017 \\
+    \hline
+  \end{tabular}
+  \label{tab:BestFitResults}
+  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry.}
+\end{table*}
+
+\subsection{The Number of Populartions in NGC 2808}
+\fidanka provides a somewhat straigtforward way to estimate the number of populations expected in a given magnitude bin given the observations.
+See Section \ref{sec:fidanka} for specific implimentaiton details.
+Here we preform an analysis of the number of populations seen in the NGC 2808 F814W-F274W vs F814W color-magnitude diagram.
+We find that for the majority of the main sequence and red giant branches BGMM prefers two populations; wherease, near the main sequnce turn off and on the majority of the subgiant branches BGMM prefers a single population model.
+
+{\color{red} Make Figure showing the BGMM fit predictions for each star vs. distance to pop mean line, does a good job of visualizing the predicted number of populations}
 
@@
 Vega magnitude system. However, we have found that the photometry has a
-systematic offset of {\color{red}$\sim0.02$ magnitudes} in the F814W band when
-compared to the same stars in the ACS survey {\color{red} [CITATION]}. The
+systematic offset of $\sim0.026$ magnitudes in the F814W band when
+compared to the same stars in the ACS survey (Figure \ref{fig:offset}). The
 exact cause of this offset is unknown, but it is likely due to a difference in
@@
 in the inferred magnitude of any fit when comparing to the ACS survey. This
-uncertainty is {\color{red} small when compared to the uncertainty in the
+uncertainty is small when compared to the uncertainty in the
 distance modulus and should not affect the conclusion of this
-paper}.
+paper.
 
-{\color{red} Figure Showing the offset}
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.90\textwidth]{src/figures/photometricOffset.pdf}
+  \label{fig:offset}
+  \caption{(left) CMD showing the photometric offset between the ACS and HUGS data for NGC 2808.
+CMDs have been randomly subsampled and colored by point density for clarity.
+(right) Mean difference between the color of the HUGS and ACS fiducual lines at the same magnitude.
+Note that the ACS data is systematically bluer than the HUGS data.}
+\end{figure*}
 
-{\color{blue}The independent analysis of the Hubble Space Telescope photometry
-ACS and HUGS, and an additional ground-based dataset created by Stetson et al.
-(2009), of the globular cluster NGC2808 resulted in findings of a systematic
-difference in the magnitude of the stars. A significant offset between the
-three datasets was found. HUGS and ACS were found to have consistent data for
-Vvega, however an offset of approximately 0.025 was found in the Ivega. ACS and
-Stetson were found to have inconsistent differences in both Vvega and Ivega.
-The three photometric studies do not match, and future studies which compare
-theoretical models to the data will need to take into account these systematic
-uncertainties. }
+The oberved photometric offset between ACS and HUGS reductions introduces a systematic uncertainity when comparing parameters derived from isochrone fits to ACS data vs those fit to HUGS data.
+Specifically, this offset introduces a {\color{red}$\sim$AGE Gyr} uncertainity.
+Moreover, for two isochrone of the same age, only seperated by helium mass fraction, a shift of the main sequence turn off of is also expected (Figure {\color{red} Figure showing MSTO location for all Ys}).
+{\color{red}Compare this to size of the MSTO shift seen here and how that informs the Y uncertainity we work with when comparing to ACS data.}

### 2023-09-01 src/sections/intro.tex
Updated with actual results finally

@@
 referred to as a Simple Stellar Population). This view was supported by
-spectroscopically uniform heavy element abundances \citep{Carretta2009}
-{\color{red}[CHECK]}, and the lack of evidence for multiple stellar populations
-(MPs) in the color-magnitude diagrams of GCs \citep{Milone2017}. However, in
+spectroscopically uniform heavy element abundances \citep{Carretta2010, Bastian2018} accross most clusters (M54 and $\omega$Cen are notable exceptions, see \citet{Marino2015} for further details), and the lack of evidence for multiple stellar populations
+(MPs) in past color-magnitude diagrams of GCs \citep[i.e.][]{Sandage1953, Alcaino1975}.
+However, over the last 40 years non-trivial star-to-star light-element abundance variations have been observed \citep[i.e.][]{Smith1987} and, in
 the last two decades, it has been definitively shown that most if not all Milky
-Way GCs have MPs \citep{Piotto2015}. The lack of photometric evidence for MPs
+Way GCs have MPs \citep{Gratton2004, Gratton2012, Piotto2015}. The lack of photometric evidence for MPs
 can be attributed to the short color throw available to ground based
-photometric surveys \citep{Milone20Here17}. While MPs are chemically distinct
+photometric surveys \citep{Milone2017}; specifically, lacking UV filters. While MPs are chemically distinct
 from one another, that distinction is most prominent when observing with $U$
@@
 brightness profile, in fact many objects which are generally thought of as GCs
-don't cleanly fit into these cuts {\color{red} EXAMPLE + CITATION}.
+don't cleanly fit into these cuts \citep{Peebles1968, Brown1991, Brown1995, Bekki2002}.
 Consequently, \citet{Carretta2010} proposed a definition of GC based on

### 2023-09-01 src/sections/modeling.tex
Added some more placeholder sections
Updated with actual results finally

@@
 mixing length grid the evolved grid of models also has dimensions population (A
-or E) and helium abundance ($Y$). Each model is evolved in DSEP's ``high
+or E) (Table \ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$). Each model is evolved in DSEP's ``high
 resolution'' mode and had a maximum allowed time step of 50 Myr.
+
+\begin{deluxetable}{c|cc||c|cc}\label{tab:comp}
+
+%% Keep a portrait orientation
+
+%% Over-ride the default font size
+%% Use Default (12pt)
+
+%% Use \tablewidth{?pt} to over-ride the default table width.
+%% If you are unhappy with the default look at the end of the
+%% *.log file to see what the default was set at before adjusting
+%% this value.
+
+%% This is the title of the table.
+\tablecaption{Population Composition}
+
+%% This command over-rides LaTeX's natural table count
+%% and replaces it with this number.  LaTeX will increment 
+%% all other tables after this table based on this number
+\tablenum{1}
+
+%% The \tablehead gives provides the column headers.  It
+%% is currently set up so that the column labels are on the
+%% top line and the units surrounded by ()s are in the 
+%% bottom line.  You may add more header information by writing
+%% another line between these lines. For each column that requries
+%% extra information be sure to include a \colhead{text} command
+%% and remember to end any extra lines with \\ and include the 
+%% correct number of &s.
+  \tablehead{\colhead{Element} & \colhead{Pop A} & \colhead{Pop E} & \colhead{Element} & \colhead{Pop A} & \colhead{Pop E} 
+}
+
+%% All data must appear between the \startdata and \enddata commands
+\startdata
+Li & -0.08 & --- & In & -1.46 & --- \\
+Be & 0.25 & --- & Sn & -0.22 & --- \\
+B & 1.57 & --- & Sb & -1.25 & --- \\
+C & 6.87 & 5.91 & Te & -0.08 & --- \\
+N & 6.42 & 6.69 & I & -0.71 & --- \\
+O & 7.87 & 6.91 & Xe & -0.02 & --- \\
+F & 3.43 & --- & Cs & -1.18 & --- \\
+Ne & 7.12 & 6.7 & Ba & 1.05 & --- \\
+Na & 5.11 & 5.7 & La & -0.03 & --- \\
+Mg & 6.86 & 6.42 & Ce & 0.45 & --- \\
+Al & 5.21 & 6.61 & Pr & -1.54 & --- \\
+Si & 6.65 & 6.77 & Nd & 0.29 & --- \\
+P & 4.28 & --- & Pm & -99.0 & --- \\
+S & 6.31 & 5.89 & Sm & -1.3 & --- \\
+Cl & -1.13 & 4.37 & Eu & -0.61 & --- \\
+Ar & 5.59 & 5.17 & Gd & -1.19 & --- \\
+K & 3.9 & --- & Tb & -1.96 & --- \\
+Ca & 5.21 & --- & Dy & -1.16 & --- \\
+Sc & 2.02 & --- & Ho & -1.78 & --- \\
+Ti & 3.82 & --- & Er & -1.34 & --- \\
+V & 2.8 & --- & Tm & -2.16 & --- \\
+Cr & 4.51 & --- & Yb & -1.42 & --- \\
+Mn & 4.3 & --- & Lu & -2.16 & --- \\
+Fe & 6.37 & --- & Hf & -1.41 & --- \\
+Co & 3.86 & --- & Ta & -2.38 & --- \\
+Ni & 5.09 & --- & W & -1.41 & --- \\
+Cu & 3.06 & --- & Re & -2.0 & --- \\
+Zn & 2.3 & --- & Os & -0.86 & --- \\
+Ga & 0.78 & --- & Ir & -0.88 & --- \\
+Ge & 1.39 & --- & Pt & -0.64 & --- \\
+As & 0.04 & --- & Au & -1.34 & --- \\
+Se & 1.08 & --- & Hg & -1.09 & --- \\
+Br & 0.28 & --- & Tl & -1.36 & --- \\
+Kr & 0.99 & --- & Pb & -0.51 & --- \\
+Rb & 0.26 & --- & Bi & -1.61 & --- \\
+Sr & 0.61 & --- & Po & -99.0 & --- \\
+Y & 1.08 & --- & At & -99.0 & --- \\
+Zr & 1.45 & --- & Rn & -99.0 & --- \\
+Nb & -0.8 & --- & Fr & -99.0 & --- \\
+Mo & -0.38 & --- & Ra & -99.0 & --- \\
+Tc & -99.0 & --- & Ac & -99.0 & --- \\
+Ru & -0.51 & --- & Th & -2.2 & --- \\
+Rh & -1.35 & --- & Pa & -99.0 & --- \\
+Pd & -0.69 & --- & U & -2.8 & --- \\
+\enddata
+
+%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
+%% or \tablecomments{text} between the \enddata and 
+%% \end{deluxetable} commands
+
+%% General table comment marker
+\tablecomments{Relative Metal composition used where a(H) = 12.
+Where the relative composition is the the same for both populations A and E it is only listed in the population A colum for the sake of visual clarity.}
+
+%% General table references marker
+\tablerefs{\citet{Milone2015}}
+
+\end{deluxetable}
 

### 2023-09-01 src/sections/results.tex
Updated with actual results finally

@@
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/BestFit.png}
+  \includegraphics[width=0.45\textwidth]{src/figures/BestFitResults.pdf}
   \label{fig:BestFitResults}
@@
 
+\begin{table*}
+  \centering
+  \begin{tabular}{c | c c c c c c}
+    \hline
+    population & age & distance modulus & extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
+    & [Gyr] & & mag & & &\\
+    \hline
+    \hline
+    A & 12.3 & 14.91 & 0.54 & 0.24 & 1.901 & 0.014\\
+    E & 14.3 & 14.96 & 0.54 & 0.39 & 1.750 & 0.017 \\
+    \hline
+  \end{tabular}
+  \label{tab:BestFitResults}
+  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry.}
+\end{table*}
+
 {\color{blue} Currently are still seeing a discontinutiy in the isochrobne below the MSTO. This must be addressed before submission.}
+
+\subsection{The Number of Populartions in NGC 2808}
+\fidanka provides a somewhat straigtforward way to estimate the number of populations expected in a given magnitude bin given the observations.
+See Section \ref{sec:fidanka} for specific implimentaiton details.
+Here we preform an analysis of the number of populations seen in the NGC 2808 F814W-F274W vs F814W color-magnitude diagram.
+We find that for the majority of the main sequence and red giant branches BGMM prefers two populations; wherease, near the main sequnce turn off and on the majority of the subgiant branches BGMM prefers a single population model.
+
+{\color{red}[FIGURE SHOWING BGMM population probability]}

### 2023-09-22 src/ms.tex
Major progress, brians second round comments

@@
 \begin{abstract}
-	Globular Clusters (GCs) provide a unique astrophysical laboratory for
-	studying the formation and evolution of stars. GCs are old, dense, and it
-	has historically been believed that they have a single stellar population. However, in the
-	last two decades, it has been definitively shown that most if not all Milky
-	Way GCs have multiple stellar populations (MPs). These MPs are chemically
-	distinct from one another, primarily separated by light element, including helium, abundance
-	variations without the standard accompanying heavy element abundance
-	variations. As the precise formation channel of these MPs remains
-	an open question, and one which is sensitive to the population - population
-	compositional differences, the extent of the composition
-	variations between MPs is a key parameter to constrain. Many metal abundances may be
-	directly measured spectroscopically; however, helium abundances are not
-	directly observable in GCs. Instead, helium abundances are inferred from
-	stellar models. It is therefore important to understand build stellar
-	models that are self-consistent in the compositions of the structure,
-	atmosphere, and opacity. In this work we present the first chemically
-	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative opacities, and AESOPUS low-temperature radiative opacities.
-	We find that the helium abundance of the second generation of stars is
-	higher than the first generation by {\color{red} SOME AMOUNT}.
-	{\color{blue} This is in agreement with previous studies of NGC 2808.}
+  The Helium abundances in the multiple populations which are now known to
+  comprise all closley studies Milky Way globular clusters are often inferred
+  by fitting isochohrones generated from from stellar evolutionary models to
+  globular cluster photometry. It is therefore important to understand build
+  stellar models that are chemically self-consistent in the compositions of the
+  structure, atmosphere, and opacity. In this work we present the first
+  chemically self-consistent stellar models of the Milky Way Globular Cluster
+  NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative
+  opacities, and AESOPUS low-temperature radiative opacities. In order to to
+  this we develope a robust software suite for globular cluster photometry,
+  \fidanka, which can be used for both population synthethis as well as
+  isochrone optimization. \fidanka's primary goal is to determine, in a
+  relativly unbiased way, the ideal number of populations within photometric
+  dataset to fit isochrones to. We achive this through a combinarion of Baysian
+  Guassian Mixture Modeling and a novel number density estimation algorithm.
+  Using \fidanka and F275W-F814W photometry from the Hubble UV Globular Cluster
+  Survey we find that the helium abundance of the second generation of stars in
+  NGC 2808 is higher than the first generation by $15\pm3\%$. This is in
+  agreement with previous studies of NGC 2808.
 \end{abstract}
+% \begin{abstract}
+% 	Globular Clusters (GCs) provide a unique astrophysical laboratory for
+% 	studying the formation and evolution of stars. GCs are old, dense, and it
+% 	has historically been believed that they have a single stellar population. However, in the
+% 	last two decades, it has been definitively shown that most if not all Milky
+% 	Way GCs have multiple stellar populations (MPs). These MPs are chemically
+% 	distinct from one another, primarily separated by light element, including helium, abundance
+% 	variations without the standard accompanying heavy element abundance
+% 	variations. As the precise formation channel of these MPs remains
+% 	an open question, and one which is sensitive to the population - population
+% 	compositional differences, the extent of the composition
+% 	variations between MPs is a key parameter to constrain. Many metal abundances may be
+% 	directly measured spectroscopically; however, helium abundances are not
+% 	directly observable in GCs. Instead, helium abundances are inferred from
+% 	stellar models. It is therefore important to understand build stellar
+% 	models that are self-consistent in the compositions of the structure,
+% 	atmosphere, and opacity. In this work we present the first chemically
+% 	self-consistent stellar models of the Milky Way Globular Cluster NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative opacities, and AESOPUS low-temperature radiative opacities.
+% 	We find that the helium abundance of the second generation of stars is
+% 	higher than the first generation by {\color{red} SOME AMOUNT}.
+% 	{\color{blue} This is in agreement with previous studies of NGC 2808.}
+% \end{abstract}
 
@@
 
-\input{src/sections/results.tex}
+% \input{src/sections/results.tex}
 

### 2023-09-22 src/sections/fidanka.tex
Major progress, brians second round comments

--- 2023-07-21 src/sections/fidanka.tex
@@
 space simultaneously. For each star in the CMD we first using a
-\texttt{introselect} partitioning algorithm to select the 50th nearest stars.
+\texttt{introselect} partitioning algorithm to select the 50 nearest stars in F814W vs. F275W-F814W space.
 To account for the case where the star is at an extreme edge of the CMD, those
@@
 populations and \fidanka's fiducial measurement routines to recover these
-populations. We run multiple tests in order to validate \fidanka's ability to
-extract varying numbers of populations without the prior of the exact population
-number. Table \ref{tab:fidankaTests} provides the parameters for each injection recovery
-test along with the $\chi^{2}$ difference between each isochrone and its associated fiducial line.
+populations. Each population was generated using the initial mass function
+given in \citep{Milone2012} for the redmost population ($\alpha=-1.2$).
+Further, every population was given a binary population fraction of 10\%,
+distance uniformly sampled between 5000pc and 15000pc, and a B-V color excess
+uniformly sampled between 0 and 0.1. Finally, each synthetic population was
+generated using a fixed age  uniformlly sampled between 7 Gyr and 14 Gyr. An
+example synthetic population along with its associated best fit isochrone are
+shown in Figure \ref{fig:ValidationBestFit}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/ExtractedIsoFit.pdf}
+  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) = 0, and an age of 12 Gyr along with the best fitting isochrone.
+The best fit paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33 Gyr.}
+  \label{fig:ValidationBestFit}
+\end{figure}
+
+For each trial we use \fidanka to measure the fiducial line and then optimize that fiducial line against the originating isochrone to esimate distance modulus, age, and color B-V excess.
+Figure \ref{fig:validationDist} is built from 1000 runs of these trials and show the mean and width of the percent error distributions for $\mu$, $E(B-V)$, and age.
+In general \fidanka is able to recover distance modulii effectively with age and E(B-V) reovery falling in line with other literature that does not cosider the CMD outside of the main sequence, main sequence turn off, sub giant, and red giant branches; specifically, it should be noted that \fidanka is not setup to model the horizontal branch.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/DistributionOfErrors.pdf}
+  \caption{Percent Error distribution for each of the three deriver parameters.
+Note that these values will be sensitive to the magnitude uncertainties of the photometry.
+Here we made use of the ACS artificial star tests to estimate the uncertanties.
+{\color{blue}Note that currently this is built with 100 runs, these take a long time so currently re running with 1000 runs.}}
+  \label{fig:validationDist}
+\end{figure}

### 2023-09-22 src/sections/fitting.tex
Major progress, brians second round comments

@@
 A and one for Population E are fit simultaneously. These isochrones are
-constrained to have distance modulus, $\mu$, and color excess, E(B-V) which agree to within 1\%.
-Moreover, we constrain the mixing length, $\alpha_{ML}$, to be constant between
-any two isochrones in a set. For every isochrone in the set of combination of
-which fulfilling these constraints $\mu$, $E(B-V)$, Age$_{A}$, and $Age_{B}$
-are optimized to reduce the $\chi^{2}$ distance between the fiducial
-lines and the isochrones. Because we fit fiducial lines directly,
-we do not need to consider the binary population fraction, $f_{bin}$, as a free
-parameter.
+constrained to have distance modulus, $\mu$, and color excess, E(B-V) which
+agree to within 1\%. Moreover, we constrain the mixing length, $\alpha_{ML}$, for any two isochrones in a set to be within 0.5 of one and other. For every isochrone in the
+set of combination of which fulfilling these constraints $\mu$, $E(B-V)$,
+Age$_{A}$, and $Age_{B}$ are optimized to reduce the $\chi^{2}$ distance
+between the fiducial lines and the isochrones. Because we fit fiducial lines
+directly, we do not need to consider the binary population fraction, $f_{bin}$,
+as a free parameter.
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/BestFitResults.pdf}
+  \includegraphics[width=0.9\textwidth]{src/figures/BestFitResults.pdf}
   \label{fig:BestFitResults}
   \caption{Best fit isochrone results for NGC 2808.}
-\end{figure}
+\end{figure*}
 
@@
 \end{table*}
+
+Past literature \citep[e.g.
+][]{Milone2015, Milone2018} have found helium mass fraction variation from the low redmost to bluemost populations of $\sim 0.12$.
+Here we find a helium mass fraction variation of 0.15 which, given the spacing of the helium grid we use \textbf{is consistent with these past results}.
 
@@
 
-The oberved photometric offset between ACS and HUGS reductions introduces a systematic uncertainity when comparing parameters derived from isochrone fits to ACS data vs those fit to HUGS data.
-Specifically, this offset introduces a {\color{red}$\sim$AGE Gyr} uncertainity.
-Moreover, for two isochrone of the same age, only seperated by helium mass fraction, a shift of the main sequence turn off of is also expected (Figure {\color{red} Figure showing MSTO location for all Ys}).
-{\color{red}Compare this to size of the MSTO shift seen here and how that informs the Y uncertainity we work with when comparing to ACS data.}
+The oberved photometric offset between ACS and HUGS reductions introduces a
+systematic uncertainity when comparing parameters derived from isochrone fits
+to ACS data vs those fit to HUGS data. Specifically, this offset introduces a
+{\color{red}$\sim$AGE Gyr} uncertainity. Moreover, for two isochrone of the
+same age, only seperated by helium mass fraction, a shift of the main sequence
+turn off of is also expected.
+Figure \ref{fig:HeMO} shows this shift.
+Note a change in the helium mass fraction of a model by 0.03 results in an approximate 0.08 magnitude shift to the main sequence turn off location.
+This means that the mean 0.026 magnitude offset we find in between ACS and HUGS data corresponds to an additional approaximate 0.01 uncertainity in the derived helium mass fraction when comparing between these two datasets.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/HeliumMeanOffset.pdf}
+  \caption{Main sequence turn off magnitude offset from a guage helium mass fraction (Y=0.30 chosen).
+All main sequence turn off locations are measured at 12.3 Gyr {\color{blue} Should I make these contour surfaces for various ages?}}
+  \label{fig:HeMO}
+\end{figure}

### 2023-09-22 src/sections/intro.tex
Major progress, brians second round comments

@@
 
-{\color{blue} NGC 2808 is the prototype globular cluster to host Multiple
-Populations.} Various studies since 2007 have identified that it may host
-anywhere from 2-5 stellar populations. These populations have been identified
-both spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}.
-Note that recent work \citep{Valle2022} calls into question the statistical significance
-of the detections of more than 2 populations in the spectroscopic data. Here we
-present new, chemically self-consistent modeling of the photometry of the two extreme populations
-of NGC 2808 identified by \citet{Milone2015}, populations A and E.
-{\color{blue} Additionally, we present a likelihood analysis of the photometric
-data of NGC 2808 to determine the number of populations present in the cluster.}
+NGC 2808 is the prototype globular cluster to host Multiple Populations.
+Various studies since 2007 have identified that it may host anywhere from 2-5
+stellar populations. These populations have been identified both
+spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}. Note
+that recent work \citep{Valle2022} calls into question the statistical
+significance of the detections of more than 2 populations in the spectroscopic
+data. Here we present new, chemically self-consistent modeling of the
+photometry of the two extreme populations of NGC 2808 identified by
+\citet{Milone2015}, populations A and E. We use archival photometry from the
+Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
+F275W and F814W passbands to charecterize multiple populations in NGC 2808
+\citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the
+photometric data of NGC 2808 to determine the number of populations present in
+the cluster.

### 2023-09-22 src/sections/modeling.tex
Major progress, brians second round comments

@@
 evolution code which includes a mixing length model of convection,
-gravitational settling, and diffusion.
+gravitational settling, and diffusion. Using the solar composition presented in
+\citep{Grevesse2007} (GAS07), MARCS model atmosphers, OPLIB high temperature
+opacities, and AESOPUS 2.0 low temperautre opacities we find a solar calibrated
+mixing length parameter, $\alpha_{MLT}$, of $\alpha_{MLT} = 1.901$.
 
@@
 above 0.7 $M_{\odot}$ we evolve a model every 0.5 $M_{\odot}$. Additionally, we
-evolve models over a grid of mixing length parameters, $\alpha_{MLT}$, from
-$\alpha_{MLT} = 1.0$ to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the
-mixing length grid the evolved grid of models also has dimensions population (A
-or E) (Table \ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$). Each model is evolved in DSEP's ``high
-resolution'' mode and had a maximum allowed time step of 50 Myr.
+evolve models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$
+to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the mixing length grid
+the evolved grid of models also has dimensions population (A or E) (Table
+\ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$).
+Each model is evolved in DSEP with typical numeric tolerences of one part in
+{\color{red}WHAT}, and an average of {\color{red} WHAT} shells. Each model is
+allowed a maximum time step of 50 Myr.
 
@@
 evolutionary points (EEPs) over a series of masses and interpolates between
-them. {\color{blue} The grid of isochrones generated for this work is avalible
-as a digital supplement to this paper.}
+them. The grid of isochrones generated for this work is avalible as a digital
+supplement to this paper. Given the complexity of the parameter space when
+fitting multiple populations along with the recent warnings in the liteerature
+regarding overfitting datasets \citep[e.g. ][]{Valle2022} we want to develop a
+more objective way of fitting isochrones to photometry than if we were to mark
+median ridge line positions by hand.

### 2023-09-22 src/sections/fidanka.tex
Began final clean up before sending to co authors

@@
 $\sim90\%$ of stars in globular clusters are younger population
-{\color{red}[CITATION]}). Based on the metallicity, $\mu$, and E(B-V) of each
+\citep[e.g.][]{Suntzeff1996, Carretta2013}). Based on the metallicity, $\mu$, and E(B-V) of each
 isochrone, bolometric corrections are taken from bolometric correction tables.
@@
 extinctions a linear interpolation is preformed between the two bounding
-values. {\color{red}[FIGURE]} shows an example of a synthetic CMD generated
-from a set of 2 NGC 2808 isochrones as well as a comparison between those
-isochrones and the measured fiducial line of the synthetic population.
+values.
 

### 2023-09-22 src/sections/fitting.tex
Began final clean up before sending to co authors

@@
 \subsection{The Number of Populartions in NGC 2808}
-\fidanka provides a somewhat straigtforward way to estimate the number of populations expected in a given magnitude bin given the observations.
-See Section \ref{sec:fidanka} for specific implimentaiton details.
-Here we preform an analysis of the number of populations seen in the NGC 2808 F814W-F274W vs F814W color-magnitude diagram.
-We find that for the majority of the main sequence and red giant branches BGMM prefers two populations; wherease, near the main sequnce turn off and on the majority of the subgiant branches BGMM prefers a single population model.
+In order to estimate the number of populations which ideally fit the NGC 2808
+F275W-F814W photometry without overfitting the data we make use of silhouette
+analysis \citep[][and in a similar manner to how \citet{Valle2022}
+preform their analysis of spectroscopic data]{ROUSSEEUW198753}. We find the average silhouette score for all tagged
+clusters identified using BGMM in all magnitude bins over the CMD using the
+standar python module \texttt{sklearn}. Figure \ref{fig:clusterAn} shows the
+silhouette analysis results and that 2 populations fit the photometry most
+ideally. This is in line with what our BGMM model predicts for the majority of
+the the CMD.
 
-{\color{red} Make Figure showing the BGMM fit predictions for each star vs. distance to pop mean line, does a good job of visualizing the predicted number of populations}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{src/figures/ClusterAnalysis.pdf}
+  \caption{Silhouette analysis for NGC 2808 F275W-F814W photometry. The Silhouette scores
+  are an average of score for each magnitude bin. Positive scores incidate that the clustering
+  algorithm produced well distinguised clusters while negative scores indicate clusters which are not
+  well distinguised.}
+  \label{fig:clusterAn}
+\end{figure}
 

### 2023-12-10 src/ms.tex
Incorperated Brian's and Greg's notes

@@
 
+\author{Amanda Ash}
+\affiliation{Department of Physics and Astronomy, University of North Georgia, Dahlonega, GA 30533, USA}
+
 \author{Rehnata Hoh}
@@
   The Helium abundances in the multiple populations which are now known to
-  comprise all closley studies Milky Way globular clusters are often inferred
-  by fitting isochohrones generated from from stellar evolutionary models to
-  globular cluster photometry. It is therefore important to understand build
-  stellar models that are chemically self-consistent in the compositions of the
-  structure, atmosphere, and opacity. In this work we present the first
-  chemically self-consistent stellar models of the Milky Way Globular Cluster
-  NGC 2808 using MARCS model atmospheres, OPLIB high-temperature radiative
-  opacities, and AESOPUS low-temperature radiative opacities. In order to to
-  this we develope a robust software suite for globular cluster photometry,
-  \fidanka, which can be used for both population synthethis as well as
-  isochrone optimization. \fidanka's primary goal is to determine, in a
-  relativly unbiased way, the ideal number of populations within photometric
-  dataset to fit isochrones to. We achive this through a combinarion of Baysian
-  Guassian Mixture Modeling and a novel number density estimation algorithm.
-  Using \fidanka and F275W-F814W photometry from the Hubble UV Globular Cluster
-  Survey we find that the helium abundance of the second generation of stars in
-  NGC 2808 is higher than the first generation by $15\pm3\%$. This is in
-  agreement with previous studies of NGC 2808.
+  comprise all closely studied Milky Way globular clusters are often inferred
+  by fitting isochohrones generated from stellar evolutionary models to
+  globular cluster photometry. It is therefore important to build stellar
+  models that are chemically self-consistent in terms of their structure,
+  atmosphere, and opacity. In this work we present the first chemically
+  self-consistent stellar models of the Milky Way Globular Cluster NGC 2808
+  using MARCS model atmospheres, OPLIB high-temperature radiative opacities,
+  and AESOPUS low-temperature radiative opacities. These stellar models were
+  fit to the NGC 2808 photometry using \fidanka, a new software tool that was
+  developed optimally fit cluster photometry to isochrones and for population
+  synthesis.  \fidanka can determine, in a relatively unbiased way, the ideal
+  number of distinct populations which exist within a dataset and then fits
+  isochrones to each population. We achieve this through a combination of
+  Bayesian Gaussian Mixture Modeling and a novel number density estimation
+  algorithm. Using \fidanka and F275W-F814W photometry from the Hubble UV
+  Globular Cluster Survey we find that the helium abundance of the second
+  generation of stars in NGC 2808 is higher than the first generation by
+  $15\pm3\%$. This is in agreement with previous studies of NGC 2808.
 \end{abstract}

### 2023-12-10 src/sections/fidanka.tex
Incorperated Brian's and Greg's notes

@@
 \section{fidanka}\label{sec:fidanka}
-When fitting isochrones to the data we have four main criteria for any method
+When fitting isochrones to the clusters with multiple populations we have four
+main criteria for any method
 
 \begin{itemize}
-	\item The method must be robust enough to work along the entire main sequence, turn off, and much of the subgiant and red giant branchs.
+  \item The method must be robust enough to work along the entire main
+    sequence, turn off, and much of the subgiant and red giant branch.
 	\item Any method should consider photometric uncertainty in the fitting process.
@@
 categories: fiducial line measurement, stellar population synthesise, and
-isochrone optimization/fitting. Additionally, there are utility functions which
+isochrone optimization/fitting. Additionally, there are utility functions that
 are detailed in the \fidanka documentation.
@@
 \fidanka takes a iterative approach to measuring fiducial lines, the first step
-of which is to make a ``guess'' as to the fiducial line. . This initial guess
+of which is to make a ``guess'' as to the fiducial line. This initial guess
 is calculated by splitting the CMD into magnitude bins, with uniform numbers of
@@
 approach, which considers the distribution of stars in both color and magnitude
-space simultaneously. For each star in the CMD we first using a
-\texttt{introselect} partitioning algorithm to select the 50 nearest stars in F814W vs. F275W-F814W space.
-To account for the case where the star is at an extreme edge of the CMD, those
-50 stars include the star itself (such that we really select 49 stars + 1). We
-use \texttt{qhull}\footnote{https://www.qhull.com}\citep{Barber1996, } to
-calculate the convex hull of those 50 points. The number density at each star
-then is defined as $50/A_{hull}$, where $A_{hull}$ is the area of the convex
-hull. Because we use a fixed number of points per star, and a partitioning
-algorithm as opposed to a sorting algorithm, this method scales like
-$\mathcal{O}(n)$, where n is the number of stars in the CMD. This method also
-intrinsically weights the density of of each star equally as the counting
-statistics per bin are uniform. We are left with a CMD where each star
-has a defined number density (Figure \ref{fig:densityMapDemo}).
+space simultaneously. For each star in the CMD we first using an
+\texttt{introselect} partitioning algorithm to select the 50 nearest stars in
+F814W vs. F275W-F814W space. To account for the case where the star is at an
+extreme edge of the CMD, those 50 stars include the star itself (such that we
+really select 49 stars + 1). We use
+\texttt{qhull}\footnote{https://www.qhull.com}\citep{Barber1996} to calculate
+the convex hull of those 50 points. The number density at each star then is
+defined as $50/A_{hull}$, where $A_{hull}$ is the area of the convex hull.
+Because we use a fixed number of points per star, and a partitioning algorithm
+as opposed to a sorting algorithm, this method scales like $\mathcal{O}(n)$,
+where n is the number of stars in the CMD. This method also intrinsically
+weights the density of of each star equally as the counting statistics per bin
+are uniform. We are left with a CMD where each star has a defined number
+density (Figure \ref{fig:densityMapDemo}).
 
@@
 algorithms we implement to fit the fiducial line to the color-density profile
-in each magnitude bin (Figure \ref{fig:densityBinsDemo}); they are explained in more detail in the \fidanka
-documentation. However, of most relevance here is the Bayesian Gaussian Mixture
-Modeling (BGMM) method. BGMM is a clustering algorithm which, for some fixed
-number of n-dimensional Gaussian distributions, $K$, determines the mean, covariance, and
-mixing probability (somewhat analogous to amplitude) of each $k^{th}$
-distribution, such that the local lower bound of the evidence of each star
-belonging strongly to a single distribution is maximized.
+in each magnitude bin (Figure \ref{fig:densityBinsDemo}); they are explained in
+more detail in the \fidanka documentation. However, of most relevance here is
+the Bayesian Gaussian Mixture Modeling (BGMM) method. BGMM is a clustering
+algorithm which, for some fixed number of n-dimensional Gaussian distributions,
+$K$, determines the mean, covariance, and mixing probability (somewhat
+analogous to amplitude) of each $k^{th}$ distribution, such that the local
+lower bound of the likelyhood of each star belonging strongly to a single
+distribution is maximized.
 
@@
 Maximization is preformed using the Dirichlet process, which is a
-non-parametric Bayesian method of determining the number of Gaussian distributions, $K$,
-which best fit the data \citep{Ferguson1973, scikit-learn}. Use of the Dirichlet process
-allows for dynamic variation in the number of inferred populations from
-magnitude bin to magnitude bin. Specifically, populations are clearly visually
-separated from the lower main sequence through the turn off; however, at the
-turn off and throughout much of the subgiant branch, the two visible
-populations overlap due to their extremely similar ages \citep[i.e.][]{Jordan2002}. The Dirichlet process allows for the BGMM method to infer a single
-population in these regions, while inferring two populations in regions where
-they are clearly separated. More generally, the use of the Dirichlet process
-removes the need for a prior on the exact number of populations to fit. Rather,
-the user specifies a upper bound on the number of populations within the
-cluster. An example bin (F814W = 20.6) is shown in Figure \ref{fig:BGMMDist}.
+non-parametric Bayesian method of determining the number of Gaussian
+distributions, $K$, which best fit the data \citep{Ferguson1973, scikit-learn}.
+Use of the Dirichlet process allows for dynamic variation in the number of
+inferred populations from magnitude bin to magnitude bin. Specifically,
+populations are clearly visually separated from the lower main sequence through
+the turn off; however, at the turn off and throughout much of the subgiant
+branch, the two visible populations overlap due to their extremely similar ages
+\citep[i.e.][]{Jordan2002}. The Dirichlet process allows for the BGMM method to
+infer a single population in these regions, while inferring two populations in
+regions where they are clearly separated. More generally, the use of the
+Dirichlet process removes the need for a prior on the exact number of
+populations to fit. Rather, the user specifies a upper bound on the number of
+populations within the cluster. An example bin (F814W = 20.6) is shown in
+Figure \ref{fig:BGMMDist}.
 
@@
 	\includegraphics[width=0.45\textwidth]{Notebooks/Figures/vertFit.png}
-	\caption{CMD where points are colored by density. Line trace the infered 
+	\caption{CMD where points are colored by density. Lines trace the infered 
 	fiducial line(s) in each magnitude bin.}
@@
 \fidanka adds a random offset to each filter based on the photometric
-uncertainties of each star. From these $n$ measurments the mean fiducial line
+uncertainties of each star. From these $n$ measurements the mean fiducial line
 for each sequence can be identified along with upper and lower bound confidence
@@
 \subsection{Stellar Population Synthesis}
-In addition to measuring fiducial lines, \fidanka also includes a stellar
-population synthesise module. This module is used to generate synthetic CMDs
-from a given set of isochrones. This is of primary importance for binary
-population modelling. The module is also used to generate synthetic CMDs for
-the purpose of testing the fiducial line extraction algorithms against priors.
+While not extensively used in this paper \fidanka can, in addition to measuring fiducial
+lines, preform stellar population synthesise. \fidanka's population synthesis
+module can generate synthetic stellar population from a set of MIST formatted
+isochrones. This is of primary importance for binary population modeling. The
+module is also used to generate synthetic CMDs for the purpose of testing the
+fiducial line extraction algorithms against priors.
 

### 2023-12-10 src/sections/fitting.tex
Incorperated Brian's and Greg's notes

@@
 We fit pairs of isochrones to the HUGS data for NGC 2808 using \fidanka, as
-descrbed in \S {\color{red}FIDANKA SECTION}. Two isochrones, one for Population
-A and one for Population E are fit simultaneously. These isochrones are
-constrained to have distance modulus, $\mu$, and color excess, E(B-V) which
-agree to within 1\%. Moreover, we constrain the mixing length, $\alpha_{ML}$, for any two isochrones in a set to be within 0.5 of one and other. For every isochrone in the
-set of combination of which fulfilling these constraints $\mu$, $E(B-V)$,
+descrbed in \S \ref{sec:fidanka}. Two isochrones, one for Population A and one
+for Population E are fit simultaneously. These isochrones are constrained to
+have distance modulus, $\mu$, and color excess, E(B-V) which agree to within
+0.5\% and an ages which agree to within 1\%. Moreover, we constrain the mixing length, $\alpha_{ML}$, for any two
+isochrones in a set to be within 0.5 of one and other. For every isochrone in
+the set of combination of which fulfilling these constraints $\mu$, $E(B-V)$,
 Age$_{A}$, and $Age_{B}$ are optimized to reduce the $\chi^{2}$ distance
+($\chi^{2} = \sum\sqrt{\Delta \text{color}^{2} + \Delta \text{mag} ^{2}}$)
 between the fiducial lines and the isochrones. Because we fit fiducial lines
@@
 
-The best fit isochrones are shown in Figure \ref{fig:BestFitResults} and optimized
-parameters for these are presented in Table \ref{tab:BestFitResults}.
-We find helium mas fractions which are consistent with those identified in past literature \citep[e.g.][]{Milone2015}.
-Note that our helium mass fraction gird has a spacing of 0.03 between grid points and we are therefore unable to resolve between certain proposed helium mass fractions for the younger sequence (for example between 0.37 and 0.39).
+The best fit isochrones are shown in Figure \ref{fig:BestFitResults} and
+optimized parameters for these are presented in Table \ref{tab:BestFitResults}.
+We find helium mass fractions that are consistent with those identified in past
+literature \citep[e.g.][]{Milone2015}. Note that our helium mass fraction grid
+has a spacing of 0.03 between grid points and we are therefore unable to
+resolve between certain proposed helium mass fractions for the younger sequence
+(for example between 0.37 and 0.39).
 
@@
   \label{fig:BestFitResults}
-  \caption{Best fit isochrone results for NGC 2808.}
+  \caption{Best fit isochrone results for NGC 2808. The best fit population A
+  and E models are shown as black lines. The following 50 best fit models are
+  presented as grey lines. The solid black line is fit to population A, while
+  the dashed black line is fit to population E.}
 \end{figure*}
@@
     \hline
-    population & age & distance modulus & extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
+    Population & Age & Distance Modulus & Extinction & Y & $\alpha_{ML}$ & $\chi^{2}_{\nu}$\\
     & [Gyr] & & [mag] & & &\\
@@
     \hline
-    A & 12.3 & 14.91 & 0.54 & 0.24 & 1.901 & 0.014\\
-    E & 14.3 & 14.96 & 0.54 & 0.39 & 1.750 & 0.017 \\
+    A & 12.996$^{+0.87}_{-0.64}$ & 15.021 & 0.54 & 0.24 & 2.050 & 0.021\\
+    E & 13.061$^{+0.86}_{-0.69}$ & 15.007 & 0.537 & 0.39 & 1.600 & 0.033 \\
     \hline
@@
   \label{tab:BestFitResults}
-  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry.}
+  \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry.
+The one sigma uncertainty reported on population age were determined from the 16th and 84th percentiles of the distribution of best fit isochrones ages.}
 \end{table*}
 
-Past literature \citep[e.g.
-][]{Milone2015, Milone2018} have found helium mass fraction variation from the low redmost to bluemost populations of $\sim 0.12$.
-Here we find a helium mass fraction variation of 0.15 which, given the spacing of the helium grid we use \textbf{is consistent with these past results}.
+Past literature \citep[e.g. ][]{Milone2015, Milone2018} have found helium mass
+fraction variation from the low redmost to bluemost populations of $\sim 0.12$.
+Here we find a helium mass fraction variation of 0.15 which, given the spacing
+of the helium grid we use \textbf{is consistent with these past results}.
 
@@
 F275W-F814W photometry without overfitting the data we make use of silhouette
-analysis \citep[][and in a similar manner to how \citet{Valle2022}
-preform their analysis of spectroscopic data]{ROUSSEEUW198753}. We find the average silhouette score for all tagged
-clusters identified using BGMM in all magnitude bins over the CMD using the
-standar python module \texttt{sklearn}. Figure \ref{fig:clusterAn} shows the
-silhouette analysis results and that 2 populations fit the photometry most
-ideally. This is in line with what our BGMM model predicts for the majority of
-the the CMD.
+analysis \citep[][and in a similar manner to how \citet{Valle2022} preform
+their analysis of spectroscopic data]{ROUSSEEUW198753}. We find the average
+silhouette score for all tagged clusters identified using BGMM in all magnitude
+bins over the CMD using the standar python module \texttt{sklearn}. Figure
+\ref{fig:clusterAn} shows the silhouette analysis results and that two
+populations fit the photometry most ideally. This is in line with what our BGMM
+model predicts for the majority of the the CMD.
 

### 2023-12-10 src/sections/fidanka.tex
Fixed broken figure labels

@@
 are uniform. We are left with a CMD where each star has a defined number
-density (Figure \ref{fig:densityMapDemo}).
+density (Figure \ref{densityMapDemo}).
 
@@
 	\includegraphics[width=0.9\textwidth]{src/figures/notebookFigures/DensityMapDemo.png}
-	\label{fig:densityMapDemo}
 	\caption{Density map demo showing density estimate over different parts of
@@
 	bottom row are colored by the density map.}
+	\label{densityMapDemo}
 \end{figure*}
@@
 algorithms we implement to fit the fiducial line to the color-density profile
-in each magnitude bin (Figure \ref{fig:densityBinsDemo}); they are explained in
+in each magnitude bin (Figure \ref{densityBinsDemo}); they are explained in
 more detail in the \fidanka documentation. However, of most relevance here is
@@
 	\includegraphics[width=0.45\textwidth]{src/figures/notebookFigures/DensityBinsDemo.png}
-	\label{fig:densityBinsDemo}
 	\caption{CMD where points are colored by density. Lines show the
@@
 	binning targeted 1000 stars per bin}
+	\label{densityBinsDemo}
 \end{figure}

### 2024-02-03 ApJ/fidanka.tex
Final copy edits of NGC 2808 paper before submission

--- 2023-12-10 src/sections/fidanka.tex
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{src/figures/notebookFigures/DensityMapDemo.png}
+	\includegraphics[width=0.9\textwidth]{src/DensityMapDemo.png}
 	\caption{Density map demo showing density estimate over different parts of
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{src/figures/notebookFigures/DensityBinsDemo.png}
-	\caption{CMD where points are colored by density. Lines show the
+	\includegraphics[width=0.45\textwidth]{src/DensityBinsDemo.png}
+	\caption{CMD where point brightness is determined by local density. Lines show the
 	density-color profile in each magnitude bin. In this figure adaptive
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{Notebooks/Figures/BGMMMixingBin.pdf}
+	\includegraphics[width=0.9\textwidth]{BGMMMixingBin.pdf}
 	\caption{Example of BGMM fit to a magnitude bin. The grey line shows the
@@
 \ref{fig:vertFit} shows the resulting fiducial line(s) in each magnitude bin
-for both a verticalized CMD and a non verticalized CMD.
+for both a verticalized CMD and a non verticalized CMD. In contrast to other
+work in the literature where evidence for up to 5 distinct populations has been
+found; we only find evidence for two stellar populations.
 
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{Notebooks/Figures/vertFit.png}
-	\caption{CMD where points are colored by density. Lines trace the infered 
-	fiducial line(s) in each magnitude bin.}
+	\includegraphics[width=0.45\textwidth]{vertFit.png}
+  \caption{Verticalized CMD where point brightness is determined by density
+  (top). CMD where point brightness is determined by density, calculated
+  fiducial lines are shown (bottom). The data used is from the Hubble Space
+  Telescope UV Legacy Survey of Galactic Globular Clusters.}
 	\label{fig:vertFit}
@@
 This method of fiducial line extraction effectively discriminated between
-multiple populations long the main sequence and RGB of a cluster, while
+multiple populations along the main sequence and RGB of a cluster, while
 simultaneously allowing for the presence of a single population along the MSTO
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/ExtractedIsoFit.pdf}
-  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) = 0, and an age of 12 Gyr along with the best fitting isochrone.
-The best fit paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33 Gyr.}
+  \includegraphics[width=0.45\textwidth]{src/ExtractedIsoFit.pdf}
+  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) =
+  0, and an age of 12 Gyr along with the best fitting isochrone. The best fit
+  paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33
+  Gyr.}
   \label{fig:ValidationBestFit}
@@
 
-For each trial we use \fidanka to measure the fiducial line and then optimize that fiducial line against the originating isochrone to esimate distance modulus, age, and color B-V excess.
-Figure \ref{fig:validationDist} is built from 1000 runs of these trials and show the mean and width of the percent error distributions for $\mu$, $E(B-V)$, and age.
-In general \fidanka is able to recover distance modulii effectively with age and E(B-V) reovery falling in line with other literature that does not cosider the CMD outside of the main sequence, main sequence turn off, sub giant, and red giant branches; specifically, it should be noted that \fidanka is not setup to model the horizontal branch.
+For each trial we use \fidanka to measure the fiducial line and then optimize
+that fiducial line against the originating isochrone to esimate distance
+modulus, age, and color B-V excess. Figure \ref{fig:validationDist} is built
+from 1000 runs of these trials and show the mean and width of the percent error
+distributions for $\mu$, $E(B-V)$, and age. In general \fidanka is able to
+recover distance modulii effectively with age and E(B-V) reovery falling in
+line with other literature that does not cosider the CMD outside of the main
+sequence, main sequence turn off, sub giant, and red giant branches;
+specifically, it should be noted that \fidanka is not setup to model the
+horizontal branch.
 
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/DistributionOfErrors.pdf}
+  \includegraphics[width=0.45\textwidth]{src/DistributionOfErrors.pdf}
   \caption{Percent Error distribution for each of the three deriver parameters.
-Note that these values will be sensitive to the magnitude uncertainties of the photometry.
-Here we made use of the ACS artificial star tests to estimate the uncertanties.
-{\color{blue}Note that currently this is built with 100 runs, these take a long time so currently re running with 1000 runs.}}
+  Note that these values will be sensitive to the magnitude uncertainties of
+  the photometry. Here we made use of the ACS artificial star tests to estimate
+  the uncertanties.}
   \label{fig:validationDist}

### 2024-02-03 ApJ/modeling.tex
Final copy edits of NGC 2808 paper before submission

--- 2023-09-22 src/sections/modeling.tex
@@
 We use the Dartmouth Stellar Evolution Program \citep[DSEP, ][]{Dotter2008} to
-generate stellar models. DSEP is a well-tested, one-dimensional stellar
+generate stellar models. DSEP is a one-dimensional stellar
 evolution code which includes a mixing length model of convection,
@@
 We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
-masses from the zero-age main sequence (ZAMS) to the tip of the red giant
+masses from the fully convective pre-main sequence to the tip of the red giant
 branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
-above 0.7 $M_{\odot}$ we evolve a model every 0.5 $M_{\odot}$. Additionally, we
-evolve models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$
-to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the mixing length grid
-the evolved grid of models also has dimensions population (A or E) (Table
-\ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$).
-Each model is evolved in DSEP with typical numeric tolerences of one part in
-{\color{red}WHAT}, and an average of {\color{red} WHAT} shells. Each model is
-allowed a maximum time step of 50 Myr.
+above 0.7 $M_{\odot}$ we evolve a model every 0.05 $M_{\odot}$. We evolve
+models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$ to
+$\alpha_{MLT} = 2.0$ in steps of 0.1. For each mixing length, a grid of models
+and isochrones were calculated, with chemical compositions consistent with
+Populations A and E (see Table \ref{tab:comp}) and a range of helium abundances
+(Y=0.24, 0.27, 0.30, 0.33, 0.36, and 0.39). In total,144 sets of isochrones,
+each with a unique composition and mixing length were calculated. Each model is
+evolved in DSEP with typical numeric tolerences of one part in $10^{7}$. Each
+model is allowed a maximum time step of 50 Myr.
 

### 2024-02-03 ArXiv/AtmopshericModels.tex
Final copy edits of NGC 2808 paper before submission

--- 2023-07-21 src/sections/AtmopshericModels.tex
@@
 \section{Chemical Consistency}\label{sec:const}
-There are three primary areas in which must the stellar models must be made chemically
-consistent: the atmospheric boundary conditions, the opacities, and interior
-abundances. The interior abundances are relatively easily handled by adjusting
-parameters within our stellar evolutionary code. However, the other two areas are
-more complicated to bring into consistency. Atmospheric boundary conditions and
-opacities must both be calculated with a consistent set of chemical abundances
-outside of the stellar evolution code.
-For evolution we use the Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008}, a well tested 1D stellar evolution code which has a particular focus on modelling low mass stars ($\le 2$ M$_{\odot}$)
+There are three primary areas in which must the stellar models must be made
+chemically consistent: the atmospheric boundary conditions, the opacities, and
+interior abundances. The interior abundances are relatively easily handled by
+adjusting parameters within our stellar evolutionary code. However, the other
+two areas are more complicated to bring into consistency. Atmospheric boundary
+conditions and opacities must both be calculated with a consistent set of
+chemical abundances outside of the stellar evolution code. For evolution we use
+the Dartmouth Stellar Evolution Program (DSEP) \citep{Dotter2008}, a well
+tested 1D stellar evolution code which has a particular focus on modelling low
+mass stars ($\le 2$ M$_{\odot}$)
 
 \subsection{Atmospheric Boundary Conditions}\label{sec:atm}
-Certain assumptions, primarily that the radiation field is at equilibirum and radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
-codes, such as DSEP, are valid when the optical depth of a star is small.
+Certain assumptions, primarily that the radiation field is at equilibrium and
+radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
+codes, such as DSEP, are valid when the optical depth of a star is large.
 However, in the atmospheres of stars, the number density of particles drops low
-enough and the optical depth consequently becomes large enough that these
-assumptions break down, and separate, more physically motivated, plasma modeling code is required.
-Generally structure code will use tabulated atmospheric boundary conditions
-generated by these specialized codes ATLAS9 \citep{Kurucz1993}, PHEONIX \citep{Husser2013}, MARCS \citep{Gustafsson2008}, and MPS-ATLAS \citep{Kostogryz2023}.
-Often, as the boundary conditions are both expensive to compute
-and not the speciality of stellar structure researchers, the boundary
-conditions are not updated as as light-element interior abundance varies.
+enough and the optical depth consequently becomes small enough that these
+assumptions break down, and separate, more physically motivated, plasma
+modeling code is required. Generally structure code will use tabulated
+atmospheric boundary conditions generated by these specialized codes, such as ATLAS9
+\citep{Kurucz1993}, PHOENIX \citep{Husser2013}, MARCS \citep{Gustafsson2008},
+and MPS-ATLAS \citep{Kostogryz2023}. Often, as the boundary conditions are
+expensive to compute, they are not updated as interior abundances vary.
 
@@
 incorporation of new atmospheric models with the same elemental abundances as
-the structure code. We use atmospheres generated from the \texttt{MARCS} grid of
-model atmospheres \citep{Plez2008}. \texttt{MARCS} provides one-dimensional,
+the structure code. We use atmospheres generated from the \texttt{MARCS} grid
+of model atmospheres \citep{Plez2008}. \texttt{MARCS} provides one-dimensional,
 hydrostatic, plane-parallel and spherical LTE atmospheric models
@@
 spectroscopically measured elemental abundances of populations A and E.
-Moreover, for each populations, atmospheres with  various helium mass fractions
-are generated. These range from Y=0.24 to Y=0.36 in steps of 0.02. A comparison
-of the pressure and temperature throughout the atmospheres of the two
-populations with helium abundances representative of literature values is shown
-in Figure \ref{fig:AEAtmComp}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{src/figures/notebookFigures/AtmosphereComparison.pdf}
-	\label{fig:AEAtmComp}
-	\caption{Comparison of the MARCS model atmospheres generated for the two
-	extreme populations of NGC 2808. These lines shows population A and E with
-	the same Helium abundance; though, we fit a grid of models over various
-	helumn abundances. Dashed lines show the temperature of the boundary
-	condition while sold lines show the pressure.}
-\end{figure}
+Moreover, for each population, atmospheres with various helium mass fractions
+are generated. These range from Y=0.24 to Y=0.36 in steps of 0.03. All
+atmospheric models are computed to an optical depth of $\tau = 100$ where their
+temperature and pressures serves as boundary conditions for the structure code.
+In general, enhancing helium in the atmosphere has only a small impact on the atmospheric
+temperature profile, while leading to a drop in the pressure by $\sim 10 - 20 \%$.
 
@@
 use OPLIB high temperature opacity tables \citep{Colgan2016} retrieved using
-the TOPS web-interface. Low temperature opacity tables are retrieved from the
-Aesopus 2.0 web-interface \citep{Marigo2009, Marigo2022}. Ideally, these
-opacities would be the same used in the atmospheric models. However, the
-opacities used in the MARCS models are not publicly available. As such, we use
-the opacities provided by the TOPS and Aesopus 2.0 web-interfaces.
+the TOPS web-interface. Retrival of High termperature opacities is done using
+\texttt{pyTOPSScrape}, first introduced in \citet{Boudreaux2023}. Low
+temperature opacity tables are retrieved from the Aesopus 2.0 web-interface
+\citep{Marigo2009, Marigo2022}. Ideally, these opacities would be the same used
+in the atmospheric models. However, the opacities used in the MARCS models are
+not publicly available. As such, we use the opacities provided by the TOPS and
+Aesopus 2.0 web-interfaces.

### 2024-02-03 ArXiv/intro.tex
Final copy edits of NGC 2808 paper before submission

--- 2023-09-22 src/sections/intro.tex
@@
 \section{Introduction}\label{sec:Intro}
-Globular clusters (GCs) are among the oldest observable objects in the
-universe \citep{Pen11}. They are characterized by high densities with typical
-half-light radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses
-ranging from $10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs
-are significantly larger than these typical values {\color{red}EXAMPLE}. GCs
-provide a unique way to probe stellar evolution \citep{Bau03}, galaxy formation
-models \citep{Boy18,Kra05}, and dark matter halo structure \citep{Hud18}.
-{\color{red} BRING IN SOME MORE RECENT CITATIONS.}
+Globular clusters (GCs) are among the oldest observable objects in the universe
+\citep{Pen11}. They are characterized by high densities with typical half-light
+radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses ranging from
+$10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs are
+significantly larger than these typical values \citep[e.g. $\omega$ Cen,
+][]{Richer1991}. GCs provide a unique way to probe stellar evolution
+\citep{Bau03}, galaxy formation models \citep{Boy18,Kra05}, and dark matter
+halo structure \citep{Hud18}.
 
-The traditional view of Globular Clusters was, for a long time, that they
-consisted of a single stellar population (SSP, in some publications this is
-referred to as a Simple Stellar Population). This view was supported by
-spectroscopically uniform heavy element abundances \citep{Carretta2010, Bastian2018} accross most clusters (M54 and $\omega$Cen are notable exceptions, see \citet{Marino2015} for further details), and the lack of evidence for multiple stellar populations
-(MPs) in past color-magnitude diagrams of GCs \citep[i.e.][]{Sandage1953, Alcaino1975}.
-However, over the last 40 years non-trivial star-to-star light-element abundance variations have been observed \citep[i.e.][]{Smith1987} and, in
-the last two decades, it has been definitively shown that most if not all Milky
-Way GCs have MPs \citep{Gratton2004, Gratton2012, Piotto2015}. The lack of photometric evidence for MPs
-can be attributed to the short color throw available to ground based
-photometric surveys \citep{Milone2017}; specifically, lacking UV filters. While MPs are chemically distinct
-from one another, that distinction is most prominent when observing with $U$
-and $B$ filters \citep{Sbordone2011}.
+The traditional view of Globular Clusters was that they consisted of a single
+stellar population (SSP, in some publications this is referred to as a Simple
+Stellar Population). This view was supported by spectroscopically uniform heavy
+element abundances \citep{Carretta2010, Bastian2018} across most clusters (M54
+and $\omega$Cen are notable exceptions, see \citet{Marino2015} for further
+details), and the lack of evidence for multiple stellar populations (MPs) in
+past color-magnitude diagrams of GCs \citep[i.e.][]{Sandage1953, Alcaino1975}.
+However, over the last 40 years non-trivial star-to-star light-element
+abundance variations have been observed \citep[i.e.][]{Smith1987} and, in the
+last two decades, it has been definitively shown that most if not all Milky Way
+GCs have MPs \citep{Gratton2004, Gratton2012, Piotto2015}. The lack of
+photometric evidence for MPs prior to the 2000, can be attributed to the more
+narrow color bands available, until very recently, to ground based photometric
+surveys \citep{Milone2017}.
 
@@
 definitions for what constitutes a globular cluster now often center the
-existence of MPs. Whereas, people have have often tried to categorized objects
+existence of MPs \citep[e.g.][]{Carretta2010}. Whereas, people have have often tried to categorized objects
 as GCs through relations between half-light radius, density, and surface
@@
 observed chemical inhomogeneities in their stellar populations. The modern
-understanding of GCs then is not simply one of a dense cluster of stars which
+understanding of GCs then is not simply one of a dense cluster of stars that
 may have chemical inhomogeneities and multiple populations; rather, it is one
@@
 however, the observed abundances of Na, Al, and Mg cannot be explained by the
-likes of the CNO cycle \citep{Prantzos2007}.
+CNO cycle \citep{Prantzos2007}. Consequently, globular cluster populations must
+be formed by some novel means.
 
@@
 
-Hot hydrogen burning (proton capture), material transport to the surface, and
+Hot hydrogen burning (i.e. proton capture), material transport to the surface, and
 material ejection into the intra-cluster media are features of each of these
@@
 
-In addition to the light-element anti-correlations observed it is also known
+In addition to the light-element anti-correlations observed, it is also known
 that younger populations are significantly enhanced in Helium
-\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
+\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, helium
 mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
-However, due to the relatively high and tight temperature range of partial
-ionization for He it cannot be observed in globular clusters; consequently, the
-evidence for enhanced He in GCs originates from comparison of theoretical
-stellar isochrones to the observed color-magnitude-diagrams of globular
-clusters. Therefore, a careful handling of chemistry is essential when modeling
-with the aim of discriminating between MPs; yet, only a very limited number of
-GCs have yet been studied with chemically self-consistent (structure and
-atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.
+However, due to both the relatively high and tight temperature range of partial
+ionization for He and the efficiency of gravitational settling in core helium
+burning stars, the initial He abundance of globular cluster stars cannot be
+observed; consequently, the evidence for enhanced He in GCs originates from
+comparison of theoretical stellar isochrones to the observed
+color-magnitude-diagrams of globular clusters. Therefore, a careful handling of
+chemistry is essential when modeling with the aim of discriminating between
+MPs; yet, only a very limited number of GCs have been studied with
+chemically self-consistent (structure and atmosphere) isochrones
+\citep[e.g.][NGC 6752]{Dotter2015}.
 
@@
 stellar populations. These populations have been identified both
-spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}. Note
+spectroscopically \citep[i.e.][]{Carretta2004, Carretta2006, Carretta2010, Gratton2011, Carretta2015, Hong2021} and photometrically \citep[i.e.][]{Piotto2007, Piotto2015, Milone2015, Milone2017, Pasquato2019}.
+Note
 that recent work \citep{Valle2022} calls into question the statistical
@@
 Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
-F275W and F814W passbands to charecterize multiple populations in NGC 2808
+F275W and F814W passbands to characterize multiple populations in NGC 2808
 \citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the

### 2024-03-22 refResponse/response.txt
Started work on ref report

# Response to the referee for the paper titled
# Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Population.

We thank the referee for their careful reading and critique of our work. Below
we have attached a response to the referees comments enumerated in the same
manner in which we recived the report. All changes to the text of the manuscript
have been placed in boldface.

# Comment 1 [Chromosome Maps]
Referee:
  Milone et al. 2015 and other groups identified five distinct populations in NGC
  2808. To do so they used the chromosome map, a color-color combination of
  filters (including F814W and F275W, the two filters used in this study). This
  diagnostic tool was introduced to maximize the separation between stars with
  different light-element abundances (different filters are in fact sensitive to
  different light-elements), information which, as demonstrated, can only be
  partially retrieved from a (F275W-F814W, F814W) CMD. The authors do not justify
  the choice to use the (F275W-F814W, F814W) CMD, instead of the chromosome map.
  Furthermore, although the authors only find two populations from their
  analysis, they do not comment on why this is the case and, importantly, how
  this compares with what Milone et al. 2015 and others found. Finally, it is
  neither clear nor physically motivated why the method used in their work should
  be a better method for identifying multiple populations than the chromosome
  map. This is a crucial point and is completely missing.
Response:
  Overall, in response to this point, we have added text to the paper to
  summarize why we elect to not make use of chromosome maps. The summary of
  that additional text is that we do not belive we have an appropriate emough
  handle on the uncertanties in the chromosome maps to allow us to make
  statistically signifigant statements about population seperation. Due to the
  manner in which chromosome maps are constructed the fractional uncertanties
  of datapoints grow rapidly when compared to what they would be in on either a
  color-magnitude diagram or color-color diagram. We investigate this and found
  that the best-case (assuming no error on the red and blue fiducial line
  positioning and only possion error on each magnitude measurment) mean
  fractional error after computing a chromosome map was > 1. (See
  https://algebrist.com/~tboudreaux/files/ChromosomeMapFractionalErrorDist.pdf
  for the probability density distribution of fractional errors over the
  chromosome map parameter space). Because Fidanka fundamentally finds clusters
  based on a mean density derived from a monte carlo sampling of the error
  space, such large uncertanties prevent fidanka from identifying clusters
  reliably. CMD space does not face the same issues. It is true that we may be
  sacrificing some of the light-element abundance-variation driven seperation
  between potential stellar populations; however, as the aim of this work is to
  identify if chemically-self consistent modeling has a signifigant affect on
  the infered helium abundance it is not strictly nessisary to extract all
  previously identified populations. Finally, as there has been recent
  literature which questions whether there are in fact more than 2 populations
  in NGC 2808 (Valle et al. 2022, based on spectroscopy) we feel that it would
  be improper to not take an extremley careful handleing of clustering and
  the uncertanties which play into it.

Referee:
  Although the authors state several times that the work adopts a chemically
  self-consistent modeling of the globular cluster, it is not explained what
  the improvement is in this work compared to previous ones. Furthermore, it is
  not clear what the chemical composition of the two populations is (in terms
  of [Fe/H], [O/Fe], [N/Fe] etc.) and what the motivation behind this choice
  is. The authors refer to Milone et al. 2015 again but without further
  explanation and it is not up to the reader to go and read that paper. The
  paper must be comprehensive and all important information used must be
  clearly mentioned and reported. Finally, that paper provides the chemical
  content of the other three multiple populations (B, C and D). Why do the
  authors specifically use the chemical content of population E? The
  motivations for this are unclear, but very important.
Response:
  There has been text added to the manuscript to clarify what we mean by
  chemically self-consistent. To summarize here, we mean that unlike the
  majority of globular cluster modeling efforts we use high temperature
  opacities, low temperature opacities, atmosphereic bounday conditions, and
  structural compositons which all agree in their atmoic mass fractions up to
  Zinc (with heavier elements being excluded as the OPLIB high-temperature
  opacity tables we use have not been computed above zinc). This has been done,
  to the best of our knowledge, for only one other cluster, NGC 6752 (Dotter et
  al. 2015). That work showed that full chemical self-consistancy did not 
  result in a signifigant change to the infered helium abundances. Here we
  are essentially reproducing this work but for another cluster which has a more
  extreme infered helium abundance in the literature. We also include text in the
  paper to explain why we use populations A and in E in specific. These two populations
  have the lowest and highest infered helium abundances respectivley and have been 
  consitantly shown to be seperable in the NGC 2808 CMD. As we are focusing on 
  determining if chemically self-consistent modeling will affect the infered helium 
  abundance it makes sense to use the most extreme models. Finally, we have included
  [Fe/H], [O/Fe], and [N/Fe] values for the two populations which we do use in the
  text of the manuscript.

Referee:
  Similar to the previous comment, the authors do not mention the literature
  values adopted as first guess for the cluster age, distance and reddening.
  They do not comment on whether there is agreement between these values and
  the best-fit parameters. This, in my opinion, is fundamental to understand
  whether the best-fit solution obtained is reliable or not.
Response:
  Text has been added to the manuscript stating what the initial guesses were
  and how these values compare to the best fit parameters. The summary of this
  is that the best fit parameters are multiple sigma removed from the initial
  guess.

Referee:
  The best-fitting isochrones for Populations A and E in Table 1 have very
  different mixing length parameters (2.050 vs 1.600). This difference has a
  significant impact on the effective temperature (especially on the red giant
  branch) and is not physically justified in the text. In fact, there is no
  obvious reason to believe that two populations in the same cluster could have
  such different mixing lengths. However, this has a huge effect on the results
  obtained. Why didn't the authors set this parameter to be the same in both
  isochrones? What would have been the results in this case?
Response:
  TBD

Referee:
  Some of the Figures they present are not easily readable and understandable,
  of which Figure 6 is an example. It is not clear how to read the
  uncertainties on the different parameters from this figure (which are not
  even reported in Table 1). Furthermore, it is not explained in the text why
  the authors use the ACS artificial star tests to derive these uncertainties,
  when they could use the same Monte Carlo approach to make robust uncertainty
  predictions for each of the parameters.
Response:
  TBD

Referee:
  While reading the paper I noticed several typos, truncated sentences and few
  unanswered questions. The authors should read through the paper and clean up
  these issues.
Response:
  We have gone through the manuscript and further copy-edited it.

### 2024-03-22 ArXiv/conclusion.tex
Started work on ref report

\section{Conclusion}\label{sec:conclusion}
Here we have preformed the first chemically self-consistent modeling of the
Milky Way Globular Cluster NGC 2808. We find that, updated atmospheric boundary
conditions and opacity tables do not have a significant effect on the inferred
helium abundances of multiple populations. Specifically, we find that
population  has a helium mass fraction of 0.24, while population E has a helium
mass fraction of 0.39. Additionally, we find that the ages of these two populations 
agree within uncertainties. Further, we only find evidence for two distinct stellar
populations, which is in agreement with recent work studying the number
of populations in NGC 2808 spectroscopic data.

Further, we introduce a new software suite for globular cluster science,
\fidanka, which has been released under a permissive open source license.
\fidanka aims to provide a statistically robust set of tools for estimating the
parameters of multiple populations within globular clusters.

### 2024-03-22 ArXiv/fidanka.tex
Final copy edits of NGC 2808 paper before submission
Started work on ref report

--- 2023-12-10 src/sections/fidanka.tex
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{src/figures/notebookFigures/DensityMapDemo.png}
+	\includegraphics[width=0.9\textwidth]{DensityMapDemo.png}
 	\caption{Density map demo showing density estimate over different parts of
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{src/figures/notebookFigures/DensityBinsDemo.png}
-	\caption{CMD where points are colored by density. Lines show the
+	\includegraphics[width=0.45\textwidth]{DensityBinsDemo.png}
+	\caption{CMD where point brightness is determined by local density. Lines show the
 	density-color profile in each magnitude bin. In this figure adaptive
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/ExtractedIsoFit.pdf}
-  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) = 0, and an age of 12 Gyr along with the best fitting isochrone.
-The best fit paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33 Gyr.}
+  \includegraphics[width=0.45\textwidth]{ExtractedIsoFit.pdf}
+  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) =
+  0, and an age of 12 Gyr along with the best fitting isochrone. The best fit
+  paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33
+  Gyr.}
   \label{fig:ValidationBestFit}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{src/figures/DistributionOfErrors.pdf}
+  \includegraphics[width=0.45\textwidth]{DistributionOfErrors.pdf}
   \caption{Percent Error distribution for each of the three deriver parameters.
-Note that these values will be sensitive to the magnitude uncertainties of the photometry.
-Here we made use of the ACS artificial star tests to estimate the uncertanties.
-{\color{blue}Note that currently this is built with 100 runs, these take a long time so currently re running with 1000 runs.}}
+  Note that these values will be sensitive to the magnitude uncertainties of
+  the photometry. Here we made use of the ACS artificial star tests to estimate
+  the uncertanties.}
   \label{fig:validationDist}

### 2024-03-22 src/sections/modeling.tex
Started work on ref report

@@
 them. The grid of isochrones generated for this work is avalible as a digital
-supplement to this paper. Given the complexity of the parameter space when
+supplement to this paper \dataset[10.5281/zenodo.10631439]{\doi{10.5281/zenodo.10631439}}. Given the complexity of the parameter space when
 fitting multiple populations along with the recent warnings in the liteerature

### 2024-03-24 refResponse/response.txt
Started incorporating ref suggestions into text of the paper

@@
 
-# Comment 1 [Chromosome Maps]
+# Comment 1 [Chromosome Maps] [TODO [ x ]]
 Referee:
@@
 
+# Comment 2 [Chemical Self-Consistency] [TODO [ x ]]
 Referee:
@@
 Response:
-  There has been text added to the manuscript to clarify what we mean by
-  chemically self-consistent. To summarize here, we mean that unlike the
-  majority of globular cluster modeling efforts we use high temperature
-  opacities, low temperature opacities, atmosphereic bounday conditions, and
-  structural compositons which all agree in their atmoic mass fractions up to
-  Zinc (with heavier elements being excluded as the OPLIB high-temperature
-  opacity tables we use have not been computed above zinc). This has been done,
-  to the best of our knowledge, for only one other cluster, NGC 6752 (Dotter et
-  al. 2015). That work showed that full chemical self-consistancy did not 
-  result in a signifigant change to the infered helium abundances. Here we
-  are essentially reproducing this work but for another cluster which has a more
-  extreme infered helium abundance in the literature. We also include text in the
-  paper to explain why we use populations A and in E in specific. These two populations
-  have the lowest and highest infered helium abundances respectivley and have been 
-  consitantly shown to be seperable in the NGC 2808 CMD. As we are focusing on 
-  determining if chemically self-consistent modeling will affect the infered helium 
-  abundance it makes sense to use the most extreme models. Finally, we have included
-  [Fe/H], [O/Fe], and [N/Fe] values for the two populations which we do use in the
-  text of the manuscript.
+  By chemically self-consistent we mean that unlike the majority of globular
+  cluster modeling efforts we use high temperature opacities, low temperature
+  opacities, atmosphereic bounday conditions, and structural compositons which
+  all agree in their atmoic mass fractions up to Zinc (with heavier elements
+  being excluded as the OPLIB high-temperature opacity tables we use have not
+  been computed above zinc). This has been done, to the best of our knowledge,
+  for only one other cluster, NGC 6752 (Dotter et al. 2015). That work showed
+  that full chemical self-consistancy did not result in a signifigant change to
+  the infered helium abundances. Here we are essentially reproducing this work
+  but for another cluster which has a more extreme infered helium abundance in
+  the literature thus showing that the NGC 6752's lack of response to self
+  consistent models is not unique to that cluster and may be expected to be a
+  more general feature of the Galactic globular cluster population. We have
+  added text to this effect in the abstract of the manuscript. We also include
+  text in the paper to explain why we use populations A and in E in specific.
+  These two populations have the lowest and highest infered helium abundances
+  respectivley and have been consitantly shown to be seperable in the NGC 2808
+  CMD. As we are focusing on determining if chemically self-consistent modeling
+  will affect the infered helium abundance it makes sense to use the most
+  extreme models. Finally, we have included a table of abundance ratios for the
+  two populations which we use in the text of the manuscript.
 
+# Comment 3 [Initial Guesses] [TODO [ ]]
 Referee:
@@
 
+# Comment 4 [Mixing Length Parameter] [TODO [ ]]
 Referee:
@@
 Response:
-  TBD
+  The mixing length traces the adiabicity of the upper atmosphere of a star,
+  encoding a complex, turbulent, 3D phenomenon. This adiabicity and the
+  turbulence should be strongly coupled to the mean molecular mass. The two
+  populations, A and E, have very different mean molecular masses due to the
+  dramatically enhanced helium abundance in population E. It is therefore not
+  suprising or at least not alarming that the mixing lengths are not in
+  agreement. We have added text to the manuscript clarifing that this
+  difference in best fit mixing lengths is not alarming.
 
+# Comment 5 [Figure Clarity] [TODO [ ]]
 Referee:
@@
 
+# Comment 6 [Copy Editing] [TODO [ ]]
 Referee:

### 2024-03-24 src/sections/fitting.tex
Fixed broken figure labels
Started incorporating ref suggestions into text of the paper

@@
   \includegraphics[width=0.9\textwidth]{src/figures/BestFitResults.pdf}
-  \label{fig:BestFitResults}
   \caption{Best fit isochrone results for NGC 2808. The best fit population A
@@
   the dashed black line is fit to population E.}
+  \label{fig:BestFitResults}
 \end{figure*}
@@
   \end{tabular}
-  \label{tab:BestFitResults}
   \caption{Best fit parameters derived from fitting isochrones to the fiducual lines derived from the NCG 2808 photometry.
 The one sigma uncertainty reported on population age were determined from the 16th and 84th percentiles of the distribution of best fit isochrones ages.}
+  \label{tab:BestFitResults}
 \end{table*}
@@
 model predicts for the majority of the the CMD.
+
+{\bf While we make use a purley CMD based approach in this work, other
+literature has made use of Chromosome Maps. These consist of implicitly
+verticalized pseudo colors. In the chromosome map for NGC 2808 there may be
+evidence for more than two populations; however, the process of transforming
+magnitude measurements into chromosome space results in dramatically increased
+uncertanties for each star. We find a mean fractional uncertantie for
+chromosome parameters of $\approx1$ when starting with magnutude
+measurements having a mean best-case (i.e. uncertainty assumed to only be due
+to Poisson statistics) fractional uncertainty of $\approx 0.0005$. Because of
+how \fidanka operates, i.e. resampling a probabilty distribution for each star
+in order to idenfify clusters, we are unable to make statisitcally meaningful
+statements from the chromosome map}
 
@@
   \includegraphics[width=0.90\textwidth]{src/figures/photometricOffset.pdf}
-  \label{fig:offset}
   \caption{(left) CMD showing the photometric offset between the ACS and HUGS data for NGC 2808.
@@
 Note that the ACS data is systematically bluer than the HUGS data.}
+  \label{fig:offset}
 \end{figure*}
@@
 to ACS data vs those fit to HUGS data. Specifically, this offset introduces a
-{\color{red}$\sim$AGE Gyr} uncertainity. Moreover, for two isochrone of the
-same age, only seperated by helium mass fraction, a shift of the main sequence
-turn off of is also expected.
-Figure \ref{fig:HeMO} shows this shift.
-Note a change in the helium mass fraction of a model by 0.03 results in an approximate 0.08 magnitude shift to the main sequence turn off location.
-This means that the mean 0.026 magnitude offset we find in between ACS and HUGS data corresponds to an additional approaximate 0.01 uncertainity in the derived helium mass fraction when comparing between these two datasets.
+$\sim 2 Gyr$ uncertainity when comparing ages between ACS and HUGS. Moreover,
+for two isochrone of the same age, only seperated by helium mass fraction, a
+shift of the main sequence turn off of is also expected. Figure \ref{fig:HeMO}
+shows this shift. Note a change in the helium mass fraction of a model by 0.03
+results in an approximate 0.08 magnitude shift to the main sequence turn off
+location. This means that the mean 0.026 magnitude offset we find in between
+ACS and HUGS data corresponds to an additional approaximate 0.01 uncertainity
+in the derived helium mass fraction when comparing between these two datasets.
 

### 2024-03-24 src/sections/intro.tex
Started incorporating ref suggestions into text of the paper

@@
 definitions for what constitutes a globular cluster now often center the
-existence of MPs. Whereas, people have have often tried to categorized objects
-as GCs through relations between half-light radius, density, and surface
-brightness profile, in fact many objects which are generally thought of as GCs
-don't cleanly fit into these cuts \citep{Peebles1968, Brown1991, Brown1995, Bekki2002}.
-Consequently, \citet{Carretta2010} proposed a definition of GC based on
-observed chemical inhomogeneities in their stellar populations. The modern
-understanding of GCs then is not simply one of a dense cluster of stars which
-may have chemical inhomogeneities and multiple populations; rather, it is one
-where those chemical inhomogeneities and multiple populations themselves are
-the defining element of a GC.
+existence of MPs \citep[e.g.][]{Carretta2010}. Whereas, people have have often
+tried to categorized objects as GCs through relations between half-light
+radius, density, and surface brightness profile, in fact many objects which are
+generally thought of as GCs don't cleanly fit into these cuts
+\citep{Peebles1968, Brown1991, Brown1995, Bekki2002}. Consequently,
+\citet{Carretta2010} proposed a definition of GC based on observed chemical
+inhomogeneities in their stellar populations. The modern understanding of GCs
+then is not simply one of a dense cluster of stars that may have chemical
+inhomogeneities and multiple populations; rather, it is one where those
+chemical inhomogeneities and multiple populations themselves are the defining
+element of a GC.
 
@@
 stellar populations. These populations have been identified both
-spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}. Note
-that recent work \citep{Valle2022} calls into question the statistical
+spectroscopically \citep[i.e.][]{Carretta2004, Carretta2006, Carretta2010,
+Gratton2011, Carretta2015, Hong2021} and photometrically
+\citep[i.e.][]{Piotto2007, Piotto2015, Milone2015, Milone2017, Pasquato2019}.
+Note that recent work \citep{Valle2022} calls into question the statistical
 significance of the detections of more than 2 populations in the spectroscopic
@@
 photometry of the two extreme populations of NGC 2808 identified by
-\citet{Milone2015}, populations A and E. We use archival photometry from the
+\citet{Milone2015}, populations A and E. {\bf We do not consider populations B,
+C, or D identified in \citet{Milone2015} as the purpose of this work is to
+identify if chemically self-consistent modelling results in a statisically
+signifigant deviation in the infered helium abundance when compared to non
+chemically self-consistent models. Use of the two populations in the NGC 2808
+with the highest identified difference between their helium populations is
+sufficent for to answer this question.}  We use archival photometry from the
 Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
-F275W and F814W passbands to charecterize multiple populations in NGC 2808
-\citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the
-photometric data of NGC 2808 to determine the number of populations present in
-the cluster.
+F275W and F814W passbands to characterize multiple populations in NGC 2808
+\citep{Milone2015, Milone2015b} (This data is avalible at MAST:
+\dataset[10.17909/T9810F]{\doi{10.17909/T9810F}}). Additionally, we present a
+likelihood analysis of the photometric data of NGC 2808 to determine the number
+of populations present in the cluster.

### 2024-03-24 src/sections/modeling.tex
Started incorporating ref suggestions into text of the paper

@@
 and isochrones were calculated, with chemical compositions consistent with
-Populations A and E (see Table \ref{tab:comp}) and a range of helium abundances
+Populations A and E (see Tables \ref{tab:comp} and \ref{tab:simpleComp}) and a range of helium abundances
 (Y=0.24, 0.27, 0.30, 0.33, 0.36, and 0.39). In total,144 sets of isochrones,
@@
 
-%% Keep a portrait orientation
-
-%% Over-ride the default font size
-%% Use Default (12pt)
-
-%% Use \tablewidth{?pt} to over-ride the default table width.
-%% If you are unhappy with the default look at the end of the
-%% *.log file to see what the default was set at before adjusting
-%% this value.
-
-%% This is the title of the table.
 \tablecaption{Population Composition}
 
-%% This command over-rides LaTeX's natural table count
-%% and replaces it with this number.  LaTeX will increment 
-%% all other tables after this table based on this number
 \tablenum{1}
 
-%% The \tablehead gives provides the column headers.  It
-%% is currently set up so that the column labels are on the
-%% top line and the units surrounded by ()s are in the 
-%% bottom line.  You may add more header information by writing
-%% another line between these lines. For each column that requries
-%% extra information be sure to include a \colhead{text} command
-%% and remember to end any extra lines with \\ and include the 
-%% correct number of &s.
   \tablehead{\colhead{Element} & \colhead{Pop A} & \colhead{Pop E} & \colhead{Element} & \colhead{Pop A} & \colhead{Pop E} 
@@
 
-%% All data must appear between the \startdata and \enddata commands
 \startdata
@@
 \enddata
-
-%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
-%% or \tablecomments{text} between the \enddata and 
-%% \end{deluxetable} commands
-
-%% General table comment marker
 \tablecomments{Relative Metal composition used where a(H) = 12.
 Where the relative composition is the the same for both populations A and E it is only listed in the population A colum for the sake of visual clarity.}
+\tablerefs{\citet{Milone2015}}
+\end{deluxetable}
 
-%% General table references marker
+\begin{deluxetable*}{c|c c c c c c c c c c c}\label{tab:simpleComp}
+
+\tablecaption{Population Abundance Ratios}
+
+\tablenum{2}
+
+  \tablehead{\colhead{Population} & \colhead{[Fe/H]} & \colhead{[$\alpha$/Fe]} & \colhead{[C/Fe]} & \colhead{[N/Fe]} & \colhead{[O/Fe]} & \colhead{[r/Fe]} & \colhead{[s/Fe]} & \colhead{C/O} & \colhead{X} & \colhead{Y} & \colhead{Z}
+}
+
+\startdata
+  A & -1.13 & 0.32 & -0.43 & -0.28 & 0.31 & -1.13 & -1.13 & 0.10 & 0.7285 & 0.2700 & 0.00154 \\
+  E & -1.13 & -0.11 & -1.39 & -0.02 & -0.66 & -1.13 & -1.13 & 0.10 & 0.7594 & 0.240 & 0.00063
+\enddata
+\tablecomments{Abundance Ratios for populations A and E in NGC 2808.}
 \tablerefs{\citet{Milone2015}}
-
-\end{deluxetable}
+\end{deluxetable*}
 
